### 2021-10-27 05_report/Manuscript_results.Rmd
PLGG Economic model
Initial commit

---
title: "Manuscript results"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r required packages}
require(tidyverse)    # for data manipulation
require(formattable)  # for formatting tables
require(knitr)        # for saving tables
require(scales)       # for ggplot axis labels
library(gridExtra)    # for gridded plots 
require(survival)     # for survival analysis
require(survminer)    # for survival plotting

```

## Data location

```{r}

fileloc <- here::here("04_analysis","output")
#fileloc <- "/Users/davidrios/OneDrive - SickKids/tomacbook"

```

The files are spread out over 5 folders.

## Table 2 & Abstract

Coding the following:

Table 2:Estimates of life-years after diagnosis, QALYs (Discounted) and Costs (Discounted) Estimates reported with 95% Confidence Interval in brackets. All costs are given in Canadian dollars.

Abstract results

```{R}
# model results 
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)
# turning into dataframe
df_model  <- map_df(res_model, readRDS)

# creating a key in the same format as the one in correct_surv
df_model <- df_model %>%
  mutate(key = paste0(sim,"_",rr))

# fixing survival for everyone who doesn't have a correct survival time
df_model <- df_model %>% 
    mutate( Value = ifelse(Variable == "LY", 80-Value, Value))

# no longer need key 
df_model <- df_model %>%
  select(-key)

df_delta <- df_model %>% 
  spread(intervention, Value) %>% 
  mutate(Delta = Norad_Fused-Rad_Fused) %>% 
  select(-Norad_Fused,-Rad_Fused)

df_model <- df_model %>% 
  group_by(Variable, Type, subset, intervention, discount, rr) %>% 
  summarise( mean = mean(Value),
             q025 = quantile(Value, 0.025),
             q975 = quantile(Value, 0.975)) %>% ungroup()
df_model <-df_model %>% 
  mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean,
                                                              symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(mean, 2))),
         q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q025, 2))),
        q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q975, 2))                  
                          )
         ) %>% 
  mutate( stat = paste0(mean, " (", q025, ";",q975,")"))

df_model1 <- df_model %>% 
  select(-mean, - q025, -q975)

df_delta1 <- df_delta %>% rename(Value = Delta) %>% 
  group_by(Variable, Type, subset, discount, rr) %>% 
  summarise( mean = mean(Value),
             q025 = quantile(Value, 0.025),
             q975 = quantile(Value, 0.975)) %>% ungroup() %>% 
  mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(mean, 2))),
         q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q025, 2))),
        q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q975, 2))

                          )
         ) %>% 
  mutate( stat = paste0(mean, " (", q025, ";",q975,")")) %>% 
    select(-mean, - q025, -q975)

df_deltacea <- df_delta %>% 
    filter(Type == "Total" | Type == "QALY", subset == "all", discount == 1 ) %>% select(-Type)  %>% spread(Variable, Delta)

df_model2 <- df_model1 %>% 
  bind_rows(mutate( df_delta1, intervention = "delta")) %>% 
    mutate(Variable = factor(Variable, levels = c("LY","QALY","Cost")),
         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE"))
         ) %>% 
  arrange(Variable, Type, discount, rr) %>% 
  spread(intervention, stat)

df_model3 <- df_model2 %>% 
  arrange(subset, rr, Variable, Type, discount )

tb2 <-df_model3  %>%
  filter(subset == "all") %>% 
  filter( !(Variable == "Cost" & discount == 0),
          !(Variable == "QALY" & discount == 0) ) %>%
  select(-Variable, - subset,-discount  ) %>% 
  rename(Variable = Type,
         Delta = delta,
         intervention = Norad_Fused,
         control = Rad_Fused)

```

**Table 2**:

```{r}
library(pander)
library(forcats)

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  select(Variable, intervention, control, Delta , rr)

pander(tb2a)
```

## Supplementary Table 1

Supplementary Table 1: Estimates of life-years after diagnosis, QALYs (Discounted) and Costs (Discounted), for fused patients, and fused patients who progressed.

```{r}

sm_tb1 <-df_model3  %>%
  filter(subset != "all") %>% 
  filter( !(Variable == "Cost" & discount == 0),
          !(Variable == "QALY" & discount == 0) ) %>%
  select(-Variable,-discount  ) %>% 
  rename(Variable = Type,
         Delta = delta,
         intervention = Norad_Fused,
         control = Rad_Fused)

sm_tb1 %>%
  kable()
```

## Figure 4 Cost-effectiveness plane

Figure 4: Cost-effectiveness plane indicating the incremental cost and incremental effectiveness estimates related to molecular testing for each probabilistic simulation assuming both a no-radiation (n = 1,000) and radiation benefit (n = 1,000)

```{r}
df_deltacea <- df_delta %>% 
    filter(Type == "Total" | Type == "QALY", subset == "all", discount == 1 ) %>% select(-Type)  %>% spread(Variable, Delta)

df_deltacea1 <- df_deltacea %>% 
  mutate(rr =factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit")),
         type = "all")
df_means <- df_deltacea %>% 
  group_by(rr) %>% 
  summarise(Cost = mean(Cost),
            QALY = mean(QALY)) %>% 
  mutate(type = "Mean Values") %>% 
  mutate(rr1 = factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit") ))
toplot_plane <-df_deltacea1 %>% 
  ggplot() + 
  geom_point(aes(x = QALY, y = Cost), alpha = 0.75 , size = 0.6) + 
  # geom_point(aes(x = QALY, y = Cost), color = "black", data = df_means,shape = 2,show.legend = TRUE, size = 3) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  theme_bw() + 
  theme(legend.title = element_blank()) +
  ylab("Discounted Total Costs") +  
  xlab("Discounted QALYs") + 
  labs(color = "", shape = "Mean") +
  scale_y_continuous(labels = dollar_format(prefix="$")) +
  facet_wrap(~ rr) + 
  theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

toplot_plane

```

# Figure 2

Figure 2: Median cumulative incidence of all-cause mortality for all patients assuming n o radiation benefit or with radiation benefit.

```{r}
res_os <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE)
df_OS <- map_df(res_os, readRDS)

df_med <- df_OS %>%
  group_by(cycle, type, intervention, rr) %>%
  summarise(median = median(OS)) %>% ungroup() %>%
   mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) %>%
    mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control"))

df_delta <- df_OS %>%
  spread(intervention, OS) %>%
  mutate(delta = (1-Norad_Fused) - (1-Rad_Fused)) %>%
  select(-Norad_Fused, - Rad_Fused) %>%
  group_by(cycle, type, rr) %>%
  summarise(median = median(delta),
            q025 = quantile(delta, 0.025),
            q975 = quantile(delta, 0.975)) %>% ungroup() %>% 
  mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit"))

rm(df_OS)

plot1 <- filter(df_med,type == "OS") %>%
  ggplot() + 
  geom_line(aes(x = cycle, y = 1-median, linetype = intervention)) +
  facet_wrap(~rr) +
  theme_bw() + 
  ylab("\n Cumulative Incidence, all-cause mortality") + 
  xlab("Time from diagnosis, Years")  + 
    theme(legend.title =element_blank(),legend.position="top") +
  theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

plot2_delta <- filter(df_delta,type == "OS" ) %>%
  mutate(t1 = "Median (95% CI)") %>% 
  ggplot() + 
  geom_line(aes(x = cycle, y = median, color = t1)) + 
  geom_ribbon(aes(x = cycle, ymin = q025, ymax = q975, fill = t1), alpha = 0.3,show.legend = T) +
  facet_wrap(~rr) + theme_bw() +
  ylab("Delta (Intervention - Control) \n Cumulative Incidence, all-cause mortality") + 
    xlab("Time from diagnosis, Years") + 
  theme(legend.title =element_blank(),legend.position="top")  +
  scale_color_manual(values = "black") +
  scale_fill_manual( values = "black") +
  theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

fig2 <-grid.arrange(plot1, plot2_delta)

fig2
```

In text results

```{r}
df_med %>% 
  filter(cycle == 20) %>% mutate(median = median*100) %>% 
  spread(intervention, median) %>% 
  arrange(rr, type) %>% filter(type == "OS" | type == "Fused") %>%  
  kable(digits = 1 ) 
```

# Supp Fig 1

Supplementary Figure 1: Cumulative incidence of all-cause mortality for all fused patients, and for fused patients who progressed

```{r}
plot2SM <-filter(df_delta,type != "OS" ) %>%
  mutate(type = factor(type, levels = c("Fused","FusedProg"),
                       labels = c("Fused patients", "Fused patients that progressed"))) %>% 
 mutate(t1 = "Median (95% CI)") %>% 
  ggplot() + 
  geom_line(aes(x = cycle, y = median, color = t1)) + 
  geom_ribbon(aes(x = cycle, ymin = q025, ymax = q975, fill = t1), alpha = 0.3,show.legend = T) +
  facet_wrap(~rr + type,) + theme_bw() +
  ylab("Delta (Intervention - Control) \n Cumulative Incidence, all-cause mortality") + 
    xlab("Time from diagnosis, Years") + 
  theme(legend.title =element_blank(),legend.position="top")  +
  scale_color_manual(values = "black") +
  scale_fill_manual( values = "black")  +
  theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

plot2SM

rm(fig2)
```

## Figure 3

Create figure 3

First accounting for mortality

```{r eval=T, message=FALSE, warning=FALSE, include=FALSE}
res_CI <- list.files(paste0(fileloc, "/res_CI"),full.names = TRUE)
res_OS <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE)

res_CI_s <- list.files(paste0(fileloc, "/res_CI"),full.names = FALSE)
res_OS_s <- list.files(paste0(fileloc, "/res_OS"),full.names = FALSE)

res_OS <- res_OS[order(res_OS_s)]
res_CI <- res_CI[order(res_CI_s)]

res_short <- list.files(paste0(fileloc, "/res_CI"),full.names = F)
res_short <- res_short[order(res_OS_s)]
v_n <-c( "neurologic", "auditory", "visual", "stroke", "cardiovascular", "SN")

## first read in first thing

for( i in seq_along(res_short)){
  if(i %% 10 == 0){message(i/length(res_short))}
tempCI <- readRDS(res_CI[i])
tempOS <- readRDS(res_OS[i]) %>% rename(time = cycle) %>% filter(type == "OS")
tempOS <-tempOS %>% group_by(type, sim , intervention, rr) %>% 
  mutate(OS_t1 = lag(OS, 1,1)) %>% 
  select(-type)

tempCI <- tempCI %>% 
  left_join(tempOS, by = c("time", "sim", "intervention", "rr"))

calcCI <- tempCI %>% 
  filter(state %in% v_n) %>%
    mutate(ci = (ceiling(ci*100000)*ceiling(OS*100000))/100000) %>% 
    mutate(ci = ceiling(ci*100000),
           OS = ceiling(OS*100000),
           OS_t1= ceiling(OS_t1*100000)/100000) %>%
  group_by(state, intervention, rr ) %>%
  mutate(ci = c(0,diff(ci,1))) %>% 
  mutate(mcf =  ci/OS,
         CI = mcf*OS_t1
         ) %>% 
  mutate(cumCI = cumsum(CI))  %>%
  select(state, intervention ,rr, time,cumCI, sim ) %>% ungroup()

for(state1 in v_n){
  dir.create(path = here::here("05_report","1newCIcalc",state1),recursive = T)

     filter(calcCI, state == state1) %>%
      saveRDS(file = here::here("05_report","1newCIcalc",state1,"/",paste0(state1,i,"BIG.RDS")))

}

}

```

```{r}
store_toplot <- vector(mode = "list", length = length(v_n))

for(j in seq_along(v_n)){
  message(j)

  list_files_instate <- list.files(here::here("05_report","1newCIcalc",v_n[j]),full.names = TRUE)

big1   <- map_df(list_files_instate, readRDS)

store_toplot[[j]] <- big1 %>% 
  group_by(intervention, state,rr) %>%
  group_by(intervention, state,rr) %>%
  mutate(cumCI = ifelse(is.nan(cumCI) , NA, cumCI  )) %>%
  fill(cumCI,.direction = "down") %>%
  group_by(intervention, state, rr,  time  ) %>%
summarise(median = median(cumCI),
          q025 = quantile(cumCI, 0.025),
          q975 = quantile(cumCI, 0.975)) %>% ungroup()

}

unlink(here::here("05_report","1newCIcalc"),recursive = T)

```

```{r}

toplotCI <- do.call(rbind,store_toplot)

plotCI <- toplotCI %>% ungroup() %>%
    mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control")) %>% 
    mutate(rr= ifelse(rr == 1, "Cherlow, et al.","No radiation benefit")) %>%
  ggplot() + 
  geom_line(aes(x = time, y = median, color = intervention)) +   geom_ribbon(aes(x = time, ymin = q025, ymax = q975 , fill = intervention), alpha = 0.3,show.legend = T) +
 facet_grid(rows =  vars(state) , cols =  vars(rr) ) +
theme_bw() +
  ylab("Cumulative incidence, Treatment related AE") + 
    xlab("Time from diagnosis, Years") + 
  theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

plotCI
```

```{r}

dir.create(here::here("05_report","tempfold1"))
res_CI <- list.files(paste0(fileloc, "/res_CI"),full.names = TRUE)
res_OS <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE)

res_CI_s <- list.files(paste0(fileloc, "/res_CI"),full.names = FALSE)
res_OS_s <- list.files(paste0(fileloc, "/res_OS"),full.names = FALSE)

res_OS <- res_OS[order(res_OS_s)]
res_CI <- res_CI[order(res_CI_s)]

res_short <- list.files(paste0(fileloc, "/res_CI"),full.names = F)
res_short <- res_short[order(res_OS_s)]

list1 <- c("stroke_gen","cardiovascular_gen","SN_gen")
list2 <- c("stroke","cardiovascular","SN")
v_n <- c(list1,list2)

## first read in first thing

for( i in 1:length(res_short)){
  if(i %% 10 == 0){message(i/length(res_short))} 
  tempCI <- readRDS(res_CI[i]) 
  tempOS <- readRDS(res_OS[i]) %>% 
    rename(time = cycle) %>% filter(type == "OS")

  tempOS <-tempOS %>% group_by(type, sim , intervention, rr) %>%
  mutate(OS_t1 = lag(OS, 1,1)) %>%
  select(-type)

tempCI <- tempCI %>%
  left_join(tempOS, by = c("time", "sim", "intervention", "rr"))

## Have TempCI joined with tempOS
## issue is that i calcualted CI = cumsum(mean(incidence*OS)) ##  mean(abs(mDur1[,ci_states[j]] - time_v[t1]) < tol)/per_alive[t1] ## cumsum(k1) ## Reversing that

calCI <-tempCI %>%
  filter(state %in% v_n) %>%
  group_by(state, sim, intervention ,rr, type) %>%arrange(time) %>%
  mutate(i = c(0, diff(ci)),
         i = (i*100000)*OS,
         ) %>% ungroup() %>%
  mutate(state = case_when(
state == list1[1] |state ==  list2[1] ~ list2[1], state == list1[2] |state ==  list2[2] ~ list2[2], state == list1[3] |state ==  list2[3] ~ list2[3]
)) %>% 
   group_by(state, sim, intervention ,rr, type, time) %>%
  mutate( i = sum(i)) %>%  ungroup() %>% 
   group_by(state, sim, intervention ,rr, type) %>%
   mutate(mcf =  i /(OS*100000),
         CI = mcf*OS_t1
         )  %>% 
    mutate(cumCI = cumsum(CI))  %>%
  select(state, intervention ,rr, time,cumCI, sim, type )

# trying to fix that cumulative incidence doesnt take into account mortality

      saveRDS(file = here::here("05_report","tempfold1",paste0(i,"BIG.RDS")),object = calCI) 
      } 
```

```{r}

file1 <- list.files(here::here("05_report","tempfold1"),full.names = T)

bigdf<-map_df(file1, readRDS)

bigdf %>% arrange(desc(cumCI))

bigdf %>% 
   mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) %>%
    mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control")) %>%
  group_by(state, intervention, rr, time,type) %>% 
  summarise(mean = mean(cumCI),
            q025 = quantile(cumCI,0.025),
            q975 = quantile(cumCI,0.975)) %>%

  ggplot() +
  facet_wrap(~state+ rr) + geom_line(aes(x = time, y= mean, color = intervention)) +
  geom_ribbon(aes(x = time, ymin = q025, ymax = q975, fill = intervention), alpha = 0.1)+
  theme_bw()

unlink(here::here("05_report","tempfold1"),recursive = T)

```

### 2021-10-27 03_ancilliary-functions/Costs.R

@@ -1,0 +1,183 @@
+## Costs function
+# Create generator for Costs
+
+gen_costs <- function(){
+  # input:
+  # output: a list with Inpatient_Costs.l , Outpatient_costs.l, AE_costs.l, Lookback_costs.l
+  # see 06_report, Tables_out for source of values
+  
+Inpatient_Costs.l <- list(
+  pre_prog = c(14955.52, 357.26),
+  prog_1 = c(3876.69, 806.4),
+  prog_2 = c(7358.42, 1367.02)) 
+  
+Outpatient_costs.l <- list(  pre_prog = c(3823.31),
+                             prog_1 = c(3786.90),
+                             prog_2 = c(3786.90))
+
+AE_cost.l <- list(Neurologic = c(30500,7400,1500),
+                  Auditory = c(8.33),
+                  Visual = c(17.95,8.98,5.98),
+                  Stroke = c(21735, 4933),
+                  Cardiac = c(20565,2997),
+                  SMN = c(4566.84,664.5))
+
+Lookback_cost.l  <- list(
+  death_plgg  =25960.21,
+  death_SN = 5494.93,
+  Dx_SN = 2842.71)
+
+
+General_pop_costs.l <- list(     five = 2383.36/12,
+                                 ten = 1412.68/12, 
+                                 fifteen = 1486.44/12, 
+                                 twenty = 1846.25/12, 
+                                 twentyfive = 1955.36/12, 
+                                 thirty = 2349.73/12, 
+                                 thirtyfive = 2618.95/12, 
+                                 fourty = 2543.75/12, 
+                                 fourtyfive = 2518.44/12, 
+                                 fifty = 2819.49/12, 
+                                 fiftyfive = 3281.00/12, 
+                                 sixty = 3948.83/12, 
+                                 sixtyfive = 4885.19/12, 
+                                 seventy = 6504.60/12, 
+                                 seventyfive = 8438.69/12, 
[…]

### 2021-10-27 03_ancilliary-functions/Effects.R

@@ -1,0 +1,195 @@
+# Effects R consists of three functions 
+# gen_effects that generates model input
+# betaPar, getting beta parameters from the mean and SE of utilities sourche
+# Effects that assigns costs
+
+# get the beta parameters from the mean and se
+require(dplyr)
+betaPar=function(m,s){
+  a <-  m * ((m * (1 - m)/s ^ 2) - 1)
+  b <-  (1 - m) * ((m * (1 - m)/s ^ 2) - 1)
+  list(a = a, b = b)
+}
+
+
+genBeta <- function(n, betaPar)
+{
+  res <- rbeta(n = n, betaPar$a, betaPar$b)
+  return(res)
+}
+
+
+
+
+
+gen_Effects <- function(deter = TRUE, 
+                        beta_Utils  ){
+  # Inputs:
+  #   deter:  Logical if deterministic or not 
+  #   list_beta_input: beta parameter inputs
+  # output: 
+  #   utilities list to be used by gen_effects
+
+# mean of a beta distribution is alpha/(alpha + beta)
+# creating deterministic mean. 
+
+if(deter){ # deterministic
+  
+  util_list <- list(
+    pre_prog        = c(beta_Utils["Children_PLGG", "mean"], beta_Utils["Adults_PLGG", "mean"]),
+    prog1           = c(beta_Utils["Children_PLGG", "mean"], beta_Utils["Adults_PLGG", "mean"]),
+    prog2           = c(beta_Utils["Children_PLGG", "mean"], beta_Utils["Adults_PLGG", "mean"]),
+    Death           = 0,
+    auditory        = c(beta_Utils["Children_auditory", "mean"], beta_Utils["Adults_auditory", "mean"]),
+    cardiovascular  =   beta_Utils["heart",       "mean"],
+    neurologic      =   beta_Utils["neurologic",  "mean"],
+    SN              =   beta_Utils["cancer_ever", "mean"],
+    stroke          =   beta_Utils["stroke",      "mean"],
+    visual          =   beta_Utils["visual",      "mean"],
+    
+    Nonpre_prog        = c(beta_Utils["NonChildren_PLGG", "mean"], beta_Utils["NonAdults_PLGG", "mean"]),
+    Nonprog1           = c(beta_Utils["NonChildren_PLGG", "mean"], beta_Utils["NonAdults_PLGG", "mean"]),
[…]

### 2021-10-27 03_ancilliary-functions/Fun_surv_est.R

@@ -1,0 +1,187 @@
+# Fun_surv_est.Rmd 
+## Est.probs.plgg
+
+
+# FunFlexFit is used by PLGG probs to estimate survival probabilities.
+
+FunFlexFit <- function(tr1, dist1, fuse1, Survdat1){
+  # FunFlex Fits estimates flexsurv survival curves
+  # Inputs
+  #   tr1: transitions
+  #   dist1: distribution to be tested
+  #   fuse1: whether fused or not fused
+  #   SurvDat1: survival data to be fitted
+  # Returns
+  #  either a flexsurv object or an error message
+
+  ret <- suppressWarnings(try( flexsurvreg(Surv(Time,   status ) ~ 1 , data = subset(Survdat1, tr == tr1 & Fusion == fuse1), dist = dist1), silent = T))
+  return(ret)
+}
+
+# EstProbs.plgg #####
+# Estimates transition probabilites
+EstProbs.plgg <- function(SurvDat, returnAll = FALSE){
+  ## Input:
+  # SurvDat: Survival data of the structure (Time, Status, Fusion)
+  # returnALL: logical indicating if to return all fits (TRUE) or only best (FALSE)
+  # Output: 
+  # BestFitsAIC a data frame with the best fitting curve (according to AIC)
+  # for the 5 transitions and fusion and non-fused status
+  # transitions: from: c(1,1,2,2,3). to c(2,4,3,4,4) 
+  
+  # Need to have these packages loaded
+  require(dfoptim , quietly = T)
+  require(flexsurv, quietly = T)
+  require(dplyr,    quietly = T)
+  require(tidyr,    quietly = T)
+  
+  # Get the names of the survival distributions
+  pos.dist <- names(flexsurv::flexsurv.dists)
+  # Remove repeated ones
+  pos.dist <- pos.dist[!(pos.dist %in% c("genf.orig","gengamma","gengamma.orig",
+                                         "weibullPH","exponential","lognormal","genf"))]
+  
+  # create a data frame to store results 
+  res.df <- SurvDat %>% 
+    dplyr::count(tr,Fusion) %>% select(-n) %>% 
+    mutate(dist = list(pos.dist)) %>% unnest(dist) 
+  res.df$flexobj <- ""
+  res.df$AIC <- ""
+  
+  
+  # For each transition,fusion status, and distribution attempt to fit a survcurv
[…]

### 2021-10-27 03_ancilliary-functions/Microsim.R

@@ -1,0 +1,286 @@
+Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_plgg,
+                            Estimated_ae,AE_outside_mat,PrMortCardio_mat, SRS_mat1, cost_input,
+                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1 ){
+  # input:  
+  # n.i: number of individuals
+  # n.y: time horizon
+  # cyc.t: cycle length
+  # monitor: Logical indicating whether to monitor 
+  # seed_n: seed number
+  # df_char: a data frame of characteristics including a column Radiation
+  # Estimated_plgg: output from EstProbs.plgg
+  # Estimated_ae: output from EstProbs.ae
+  # AE_outside_mat: output from AE_outside_pr
+  # PrMortCardio_mat: output from MortCardio_est
+  # SRS_mat1: output from SRS_gen
+  # output: 
+  # list of model run outcomes with the same parameters but varying intervention
+  
+  # This function runs the microsimulation and is structured in a similar manner as the 
+  # DARTH Microsimualtion format. It consists of X sections:
+  # 1. Model inputs: brining into function evironment model inputs
+  # 2. Initializing: creating matrices to store simulation results
+  # 3. Initial cycle: information on status at cycle 1 and costs and utilities associated 
+  # 4. Cycle 2- End: Modelling natural history, costs, utilities, and radiation decision
+  # 5. Summarizing: Summarizing model results 
+  # Sections 2-5, are done for intervention and control  
+  
+  
+  #1. Model inputs -----
+  # Due to scoping issues have to create some variables as global variables.  
+  n.i <<- n.i      # number of individuals
+  cyc.t <<- cyc.t  # cycle length (1/12)
+  n.y <<- n.y      # max cycle
+  v.n  <<-  c("pre_prog", "prog1","prog2","death_plgg",  # PLGG related
+              "neurologic","auditory","visual","stroke", # Treatment related AE
+              "cardiovascular","SN", 
+              "stroke_gen", "cardiovascular_gen","SN_gen", # General population risk of AE
[…]

### 2021-10-27 03_ancilliary-functions/MicrosimScenario.R

@@ -1,0 +1,285 @@
+# MicrosimScenario.R
+Microsimulation_scenario <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_plgg,
+                                     Estimated_ae,AE_outside_mat,PrMortCardio_mat, SRS_mat1, cost_input,
+                                     util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1, prob_scenario ){
+  # input:  
+  # n.i: number of individuals
+  # n.y: time horizon
+  # cyc.t: cycle length
+  # monitor: Logical indicating whether to monitor 
+  # seed_n: seed number
+  # df_char: a data frame of characteristics including a column Radiation
+  # Estimated_plgg: output from EstProbs.plgg
+  # Estimated_ae: output from EstProbs.ae
+  # AE_outside_mat: output from AE_outside_pr
+  # PrMortCardio_mat: output from MortCardio_est
+  # SRS_mat1: output from SRS_gen
+  # output: 
+  # list of model run outcomes with the same parameters but varying intervention
+  
+  # This function runs the microsimulation and is structured in a similar manner as the 
+  # DARTH Microsimualtion format. It consists of X sections:
+  # 1. Model inputs: brining into function evironment model inputs
+  # 2. Initializing: creating matrices to store simulation results
+  # 3. Initial cycle: information on status at cycle 1 and costs and utilities associated 
+  # 4. Cycle 2- End: Modelling natural history, costs, utilities, and radiation decision
+  # 5. Summarizing: Summarizing model results 
+  # Sections 2-5, are done for intervention and control  
+  
+  
+  #1. Model inputs -----
+  # Due to scoping issues have to create some variables as global variables.  
+  n.i <<- n.i      # number of individuals
+  cyc.t <<- cyc.t  # cycle length (1/12)
+  n.y <<- n.y      # max cycle
+  v.n  <<-  c("pre_prog", "prog1","prog2","death_plgg",  # PLGG related
+              "neurologic","auditory","visual","stroke", # Treatment related AE
+              "cardiovascular","SN", 
[…]

### 2021-10-27 03_ancilliary-functions/Probs.R

@@ -1,0 +1,395 @@
+# Probs.R
+
+Probs <- function( M_it, D_m,  df.i, Vis_m, CycleLength, GlobT, EstPLGG, EstAE,
+                   AE_outside_mat1,PrMortCardio_mat1,SRS_mat, curent_age_v,rad_benefit1){
+  # input: 
+  # M_it: a numeric vector indicating current state 
+  # D_m: matrix (numeric) indicating the duration of stay in each state
+  # df.i: data.frame of cohort characteristics
+  # Vis_m: a matrix indicating whether a patient has visited a specific state
+  # CycleLength: numeric length of cycle
+  # GlobT: global time
+  # EstPLGG: output from EstProbs.plgg
+  # EstAE: output from EstProvs.ae
+  # AE_outside_mat1: output from AE_outside_pr
+  # PrMortCardio_mat: a matrix indicating probaility of Cardiovascular related mortality
+  # SRS_mat: SRS_mat
+  # output  
+  #  m.p.it: a matrix of dim number of individuals,number of states  
+  #           where the i,jth element is the probability
+  #           of transitioning from the current state to state j for individual i
+  
+  
+  # First create empty vector that i'll be adding to
+  m.p.it <- matrix(0, n.i, n.s)   
+  colnames(m.p.it) <- v.n
+  
+  # Identify which cases (if any ) are fused
+  FusedLog <- df.i$Fusion == 1
+  anyFused <- any(FusedLog)
+  # Do the same for Radiation
+  RadIndc <- df.i$Radiation == 1
+  
+  
+  # Identifying which PLGG related state each patient is in not counting death
+  # Can do this sequentially since patients go from pre-prog to prog 1 than prog 2
+  plgg.it <- rowSums(D_m[,c("pre_prog","prog1","prog2")] > 0 )
+  plgg.char  <- c("pre_prog","prog1","prog2")[plgg.it]
+  
+  
+  # Identify time in state for the most recent progression. 
+  # This requiers some interesting subsetting. 
+  # Basically when we collpase D_m as a vector it does so by rows which we can
+  # correct index values using plgg.timein. This make sense if you do a simple test
+  plgg.timeinstate <- as.vector(D_m[,c(1,2,3)])[(plgg.it-1)*n.i + 1:n.i]
+  
+  # Get errors if attempt to do this with empty vectors
+  # so must have atleast some fused patients
+  
[…]

### 2021-10-27 03_ancilliary-functions/Radiation-Benefit.R

@@ -1,0 +1,94 @@
+# Radiation Benefit
+
+# This R script creates a function to generate deterministic and bootstrapped radiation fitting
+# fitsdistributions
+
+FunFlexFit1 <- function(tr1, dist1,  Survdat1){
+  # FunFlex Fits estimates flexsurv survival curves
+  # Inputs
+  #   tr1: transitions
+  #   dist1: distribution to be tested
+  #   fuse1: whether fused or not fused
+  #   SurvDat1: survival data to be fitted
+  # Returns
+  #  either a flexsurv object or an error message
+
+  ret <- suppressWarnings(try( flexsurvreg(Surv(time,   status ) ~ 1 , data = Survdat1 , dist = dist1), silent = T))
+  return(ret)
+}
+
+
+
+## Read data
+### Input to move over
+# dig_radbenefit <- readRDS(here::here("02_data","cherlow_dig.RDS"))
+# allows for a decrease in radiation benefit
+
+
+fun_genRadBenefit <- function(dig_radbenefit, deter){
+  # digitized_radbenefit: digitized data from cherlow
+  # deter : a logical indicating if deterministic
+  # requires: flexsurv
+require(flexsurv, quietly = T)
+require(dplyr)
+pos.dist <- names(flexsurv::flexsurv.dists)
+  # Remove repeated ones
+pos.dist <- pos.dist[!(pos.dist %in% c("genf.orig","gengamma","gengamma.orig",
+                                         "weibullPH","exponential","lognormal","genf"))]
+
+
+# Storing data  
+res1  <- data.frame(post.dist = pos.dist, tr  = 2)
+res1$AIC <- Inf
+res1$flexobj <-""
+res1$post.dist <- as.character(res1$post.dist)
+# if determiistic no bootstrapping
+if(deter){
+  
+  for(j in seq_along(res1$post.dist)){
+    
+    fit1 <- FunFlexFit1(tr1 = res1$tr[j], dist1 = res1$post.dist[j], Survdat1 = dig_radbenefit)
+    
+    if(typeof(fit1) != "character"){
+      res1$flexobj[[j]] <- list( fit1)
+      res1$AIC[[j]] <- fit1$AIC  
+    } else{
+      res1$flexobj[[j]] <- NA
+      res1$AIC[[j]]  <- NA
+    }
+    
[…]

### 2021-10-27 03_ancilliary-functions/ae_functions.R

@@ -1,0 +1,216 @@
+# ae_functions.R
+AE_outside_pr <-function(Rate_cancer.RDS,
+                         Rate_cardio.RDS,
+                         Rate_stroke.RDS,
+                         life_exp_minus.RDS,
+                         life_exp_smn.RDS,
+                         cycles_inyear){
+  
+  # input: Rate_cancer.RDS created by AE-data-processing.Rmd ( in 01_data_raw)
+  #        Rate_cardio.RDS created by AE-data-processing.Rmd ( in 01_data_raw)
+  #        Rate_stroke.RDS created by AE-data-processing.Rmd ( in 01_data_raw)
+  #         life_exp_minus.RDS created by AE-data-processing.Rmd ( in 01_data_raw)
+  #        cycles_inyear: number of cycles in a year (must be min of 1)
+  # output: return_mat a matrix, with the first collumn being seq(0, 110, by = cycle_inyear )
+  #         the second collumn being probability of stroke during that cycle,
+  #         3rd probaiblity of cardiovascular, and 4th probability of cancer event, 5th probability
+  #         of outside risk of death
+  
+  
+  require(dplyr)
+  ## Currently all data is rate per 100000, between age X and X +1 
+  ## Turning into probabilities
+  ## First by dividing rate by 100000 to get a rate per person year
+  ## Dividing by 12 to get a rate by person month
+  ## Turning into a probability
+  
+  vect_time <- seq(0, 110, by =1/cycles_inyear)
+  
+  Pr_cancer <- Rate_cancer.RDS %>% 
+    mutate(rate_person = Rate_100000/100000,
+           rate_cylce = rate_person/cycles_inyear,
+           pr_cycle  = 1-exp(-rate_cylce))
+  
+  Pr_cancer_vect <- vector(mode = "numeric", length = length(vect_time))
+  
+  for( i in 1:dim(Pr_cancer)[1]){
+    Pr_cancer_vect[ vect_time >= Pr_cancer$AgeStart[i] & vect_time <Pr_cancer$AgeEnd[i]] <- Pr_cancer$pr_cycle[i]
+  }
+  
[…]

### 2021-10-27 03_ancilliary-functions/gen_synpop.R

@@ -1,0 +1,9 @@
+gen_synpop <- function(l1, n1=  100000){
+  #l1: list of mean ,sd agedx, and neseted glms fit to fusion and sex
+  
+ret<-  data.frame(AgeDx = round(runif(n = n1, min = 0,max = 18)),
+             Sex = as.numeric(runif(n= n1, min= 0,max =1) < 0.4931129),
+             Fusion = as.numeric(runif(n= n1, min = 0, max =1 ) < 0.3581267)
+             )
+    return(ret)
+}

### 2021-10-27 03_ancilliary-functions/microsim-helpers.R

@@ -1,0 +1,235 @@
+# Made a small modification where the simulation runs using numeric state indicators not colnames.
+
+# Replaced lev <- dimnames(m.p) to lev <- 1:length(dimnmaes) 
+# Function to run the vectorized version of microsimulation 
+
+samplev2 <- function (probs, m) {
+  d <- dim(probs)
+  n <- d[1]
+  k <- d[2]
+  lev <- dimnames(probs)[[2]]
+  if (!length(lev)) 
+    lev <- 1:k
+  ran <- matrix(lev[1], ncol = m, nrow = n)
+  U <- t(probs)
+  for(i in 2:k) {
+    U[i, ] <- U[i, ] + U[i - 1, ]
+  }
+  if (any((U[k, ] - 1) > 1e-05))
+    stop("error in multinom: probabilities do not sum to 1")
+  
+  for (j in 1:m) {
+    un <- rep(runif(n), rep(k, n))
+    ran[, j] <- lev[1 + colSums(un > U)]
+  }
+  ran
+}
+
+# Fun.GenI generates individuals. Need the file location of the analysis set and 
+# the number to generate. NumToGen == n.i
+
+
+## tempdat$Sex = 0 
+## tempdat$Sex[tempdat$Gender == male]  =1 
+## although I am not sure why you set NAs equal to zero
+
+Fun.GenI<- function(loc.analysis.set,NumToGen, Seed_n1){
+  # input: 
+  set.seed(Seed_n1)
+  
+  tempdat   <- readRDS(loc.analysis.set)$df.diagnosis
+  tempdat <- tempdat[,c("Fusion","AgeDx", "Gender")]
+  tempdat$Sex <- 0
+  tempdat$Sex[tempdat$Gender == "male"] <- 1
+  tempdat <- tempdat[,c("Fusion","AgeDx","Sex")]
+  tempdat <- tempdat[sample(x = 1:dim(tempdat)[1], size = NumToGen, replace = T),]
+  return(tempdat)
+}
+
+# SurvProbFun ####
+# This is the guts of the flexsurv summary function made to create probabilities
+# that are vectorized. Not commented if interested run once with debug
+SurvProbFun <- function(object, t , cycle1){
+  start  = t - cycle1 
+  x <- object
+  dat <- x$data
+  fn <-  function(t,start,...) {
+    s_t <-(1 - x$dfns$p(start,...))
+    s_t1 <- (1 - x$dfns$p(t,...))
[…]

### 2021-10-27 03_ancilliary-functions/summary.R

@@ -1,0 +1,239 @@
+### Summary function
+
+# function of the following inputs
+sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
+                         costsplgg, costsAE, util, vRAD, vFusion  ){
+# What simulation number,
+# Parameter on radiation benefit
+# Intervention
+#sim_num = 1
+#intervention1 = "Intervention"
+#rr1 = 0
+# d_rate <- 0.00246627
+v_dwc <- 1 / (1 + d_rate) ^ (0:(dim(mM)[2]-1))   # calculate the cost discount weight based on the discount rate d.c 
+cyc_length <- 1/12
+max_age <- 80
+## Requires
+require(dplyr)
+require(stringr)
+
+
+
+# output
+
+res_ly <- vector(mode = "numeric", length = 3)
+type <-c("all","fused","fused_rad")
+
+## Matrix of model inputs
+# LY 
+#   All
+res_ly[[1]] <- mean(rowSums(util == 0)*cyc_length)
+#   Fused
+res_ly[[2]] <- mean(rowSums(util[vFusion == 1,] == 0)*cyc_length)
+#   Fused and Prog 1 
+res_ly[[3]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],] == 0)*cyc_length)
+
+df_LY <- tibble(Value = res_ly,  Variable = "LY", Type = "LY" ,  subset = type , discount = 0)
+
+res_qaly <- vector(mode = "numeric", length = 6)
+# QALY 
+#   All
+res_qaly[[1]] <- mean(rowSums(util*cyc_length*v_dwc))
+#   Fused
+res_qaly[[2]] <- mean(rowSums(util[vFusion == 1,]*cyc_length*v_dwc))
+#   Fused and Prog 1 
+res_qaly[[3]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],]*cyc_length*v_dwc))
+
+# QALY - undiscounted 
+#   All
+res_qaly[[4]] <- mean(rowSums(util*cyc_length))
+#   Fused
+res_qaly[[5]] <- mean(rowSums(util[vFusion == 1,]*cyc_length))
+#   Fused and Prog 1 
+res_qaly[[6]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],]*cyc_length))
+
+
+df_QALY <- tibble(Value = res_qaly, Variable = "QALY", Type = "QALY",
[…]

### 2021-10-27 04_analysis/Cost-effectiveness_basecase.R

@@ -1,0 +1,186 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
+#PrDeath_Stroke: Probability of death related to stroke AE
[…]

### 2021-10-27 04_analysis/Cost-effectiveness_scenario.R

@@ -1,0 +1,215 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/outputscenario/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/MicrosimScenario.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
+#PrDeath_Stroke: Probability of death related to stroke AE
+#RSR_gen: ratios of RSR ratios 
+
[…]

### 2021-10-28 03_ancilliary-functions/gen_synpop.R
added correlation structure to synthetic population
Introduced correlation structure to synthetic population

@@ -1,9 +1,43 @@
-gen_synpop <- function(l1, n1=  100000){
+gen_synpop <- function( n1=  100000, deter = T){
   #l1: list of mean ,sd agedx, and neseted glms fit to fusion and sex
+    if(deter = T){
+  AgeDx = round(runif(n = n1, min = 0,max = 18))
+  coef1 <- c(0.03758116, -0.006658198) # intercenpt + AgeDx, binomial 
+  o1 <- exp(cbind(1, AgeDx) %*% coef1)
+  Sex = rbinom(n1,1, prob = o1/(1+o1))
+  coef2 <- c(0.1107713, -0.05921511, -0.2586516) # interept + Agedx + Sex
   
-ret<-  data.frame(AgeDx = round(runif(n = n1, min = 0,max = 18)),
-             Sex = as.numeric(runif(n= n1, min= 0,max =1) < 0.4931129),
-             Fusion = as.numeric(runif(n= n1, min = 0, max =1 ) < 0.3581267)
-             )
+  o2 <- exp(cbind(1, AgeDx,Sex) %*% coef2)
+  Fusion =  rbinom(n1,1, prob = o2/(1+o2))
+  
+  
+  ret<-  data.frame(AgeDx = AgeDx,
+             Sex = Sex,
+             Fusion = Fusion)
+
+  } else{
+    coef1<- mvtnorm::rmvnorm(n = 1,mean = c(0.03758116, -0.006658198), sigma =
+                               matrix(c(0.05869754, -0.004873916, -0.004873916, 0.0004982868), nrow = 2) )
+    coef2<- mvtnorm::rmvnorm(n = 1,mean = c(0.1107713, -0.05921511, -0.2586516), sigma =
+                               matrix(c(0.07417177, -0.005295126, -0.02501394,
+                                        -0.005295126, 0.0005518633, 0.0001718476,
+                                        -0.02501394, 0.0001718476, 0.04914024), nrow = 3) )
+    
+    AgeDx = round(runif(n = n1, min = 0,max = 18))
+    o1 <- exp(cbind(1, AgeDx) %*% t(coef1))
+    Sex = rbinom(n1,1, prob = o1/(1+o1))
+    o2 <- exp(cbind(1, AgeDx,Sex) %*% t(coef2))
+    Fusion =  rbinom(n1,1, prob = o2/(1+o2))
+    
+    
+    ret<-  data.frame(AgeDx = AgeDx,
[…]

### 2023-12-05 04_analysis/control scenarios/Bryans SickKids data/chart_audit_survival_new_controls_firstline.Rmd
updated to targeted first line

---
title: "Survival Analysis Chart Audit Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(survival)
library(flexsurv)
library(survminer)
library(here)
library(darthtools)
library(data.table)
```

- date last FU CCO gone
- age_diag same as age_diag_years

```{r}
loc_here <- getwd()
# df0 <- read_csv(paste0(loc_here, "02_data/PLGG_targeted_chartaudit_form.csv"), skip=1)
# df <- read_csv("plgg_cea_controls.csv")
df <- read_csv("PLGG_targetedtherapy_CEA_Petros_Nov2023_firstline.csv")
df$status <- ifelse(df$secondprogress   == 1 | df$death == 1, 1 ,0)
df$time <- df$TimetoOutcome_days /365 # change time in days to in years
```

Kaplan-Meier estimates of PFS

```{r}
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = status) ~ 1, data = df)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = df,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = F,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in years', # Change X-axis label
  title      = "Survival curve for PFS",
  subtitle   = "Based on Kaplan-Meier estimates"
)
```

# Fit survival curves:

*Control arm:*

```{r}
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gengamma", "rps")
fit_control <- fit.fun(time="time", status="status", mods=mods, 
                       data=df %>% as.data.frame(), times=times,
                       extrapolate = T) 
a <- fit_control$plot
a$plot <- a$plot + labs(subtitle="Control arm (n=34)") + scale_x_continuous(breaks=seq(0,80,10))
a$plot
```

Choose best-fitting survival model:

```{r}
GoF_control <- data.frame(AIC = fit_control$AIC, BIC = fit_control$BIC)
choose_PFS_AIC_control <- rownames(GoF_control)[which.min(GoF_control$AIC)]; choose_PFS_AIC_control
choose_PFS_BIC_control <- rownames(GoF_control)[which.min(GoF_control$BIC)]; choose_PFS_BIC_control
```

```{r}
mods <- c("gamma", "exp")
fit_control <- fit.fun(time="time", status="status", mods=mods, 
                       data=df %>% as.data.frame(), times=times,
                       extrapolate = T) 
a1 <- fit_control$plot
a1$plot <- a1$plot + labs(subtitle="Control arm (n=34), best-fitting curve") + 
  scale_x_continuous(breaks=seq(0,80,10))
a1$plot
```

Calculate transition probabilities (prog 1 to prog 2):

```{r}
best_model_control <- fit_control$model.objects$models$`Exponential`
surv_probs_control <- surv_prob(best_model_control, times = times) # surv probs (not having 2nd prog) from prog 1
trans_probs_control <- trans_prob(surv_probs_control) # transition probs from prog 1 to prog 2
```

Bootstrap for microsim:

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(df), replace=T)
  PFS_data_boot <- df[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "status", 
                     data = PFS_data_boot %>% as.data.frame(),
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_sk_firstline.RData")
```

```{r}

```

### 2023-12-05 04_analysis/control scenarios/Erics firstline RCT/first_line_paper_survival.Rmd
updated to targeted first line

---
title: "PFS analysis of paper - first line"
output:
  pdf_document: default
  html_document: default
---

Paper:

https://pubmed.ncbi.nlm.nih.gov/37733309/#:~:text=Conclusions%3A%20Among%20pediatric%20patients%20with,chemotherapy%20as%20first%2Dline%20therapy

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, eval = TRUE)
rm(list = ls())     # clear memory (removes all the variables from the workspace)
options(scipen=999) # disable scientific notation
```

```{r, warning=F, message=F}
if (!require('pacman')) install.packages('pacman'); library(pacman) # use this package to conveniently install other packages
# load (install if required) packages from CRAN
p_load("here", "dplyr", "devtools", "gems", "flexsurv", "flexsurvcure", "survHE", "survminer", "ggplot2", "msm", "igraph", "mstate", "reshape2", "knitr", "abind", "dampack", "data.table", "tm")

# load (install if required) packages from GitHub
# install_github("DARTH-git/darthtools", force = TRUE) Uncomment if there is a newer version
p_load_gh("DARTH-git/darthtools")
```

# 04 Digitized Data

Use the function `digitise()` to translate the digitised OS and PFS data into patient level information.

## Control arm

```{r}
time_interval <- seq(0, 32, by = 2)
at_risk <- c(37,25,19,17,10,7,4,2,1,1,1,1,0,0,0,0,0)
surv_data <- read.csv("out_put_alanNejmoa.png_Auto_Digitized.csv", header = T)
surv_data <- surv_data[surv_data$curve==2,]
surv_data$St <- surv_data$St/100
surv_data <- data.frame(k = 1:nrow(surv_data),
                        Time = surv_data$time,
                        Sk = surv_data$St)
write.table(surv_data, file = "first_line_PFS_curve_control.txt", row.names = F)
surv_data <- read.table("first_line_PFS_curve_control.txt", header = T)
surv_times <- surv_data$Time

n_risk_table <- create_at_risk_table(survival_time = surv_times,
                                     Years = time_interval,
                                     AtRisk = at_risk)
write.table(n_risk_table, "first_line_PFS_risktable_control.txt", row.names = F)
```

```{r, results="hide"}
# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
digitise(surv_inp   = "first_line_PFS_curve_control.txt", 
         nrisk_inp  = "first_line_PFS_risktable_control.txt", 
         km_output  = "first_line_PFS_KM_control.txt", 
         ipd_output = "first_line_PFS_IPD_control.txt")

# Link the IPD files across the two arms of the trial for OS and PFS
IPD_PFS <- make.ipd(ipd_files = c("first_line_PFS_IPD_control.txt"), ctr = 1,
                    var.labs  = c("time","event","arm"))
IPD_PFS <- IPD_PFS %>% select(-arm)
```

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
  title      = "Survival curve for PFS, Control arm",
  subtitle   = "Based on Kaplan-Meier estimates"
)
```

```{r}
surv_data$Time <- surv_data$Time/12 # change time in months to years
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods) 
```

```{r}
GoF_PFS <- data.frame(AIC = fit_PFS$AIC, BIC = fit_PFS$BIC)
choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$AIC)]; choose_PFS
choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$BIC)]; choose_PFS
```

```{r}
mods=c("lnorm", "exp")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods=mods) 
```

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("lnorm"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$`log-Normal`
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_firstline.RData")
```

## Targeted arm

```{r}
time_interval <- seq(0, 32, by = 2)
at_risk <- c(73,67,64,62,49,40,33,25,23,13,11,7,4,3,2,2,0)
surv_data <- read.csv("out_put_alanNejmoa.png_Auto_Digitized.csv", header = T)
surv_data$St <- surv_data$St/100
surv_data <- surv_data[surv_data$curve==1,]
surv_data <- data.frame(k = 1:nrow(surv_data),
                        Time = surv_data$time,
                        Sk = surv_data$St)
write.table(surv_data, file = "first_line_PFS_curve_targeted.txt", row.names = F)
surv_data <- read.table("first_line_PFS_curve_targeted.txt", header = T)
surv_times <- surv_data$Time

n_risk_table <- create_at_risk_table(survival_time = surv_times,
                                     Years = time_interval,
                                     AtRisk = at_risk)
write.table(n_risk_table, "first_line_PFS_risktable_targeted.txt", row.names = F)
```

```{r, results="hide"}
# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
digitise(surv_inp   = "first_line_PFS_curve_targeted.txt",
         nrisk_inp  = "first_line_PFS_risktable_targeted.txt",
         km_output  = "first_line_PFS_KM_targeted.txt",
         ipd_output = "first_line_PFS_IPD_targeted.txt")

# Link the IPD files across the two arms of the trial for OS and PFS
IPD_PFS <- make.ipd(ipd_files = c("first_line_PFS_IPD_targeted.txt"), ctr = 1,
                    var.labs  = c("time","event","arm"))
IPD_PFS <- IPD_PFS %>% select(-arm)
```

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
  title      = "Survival curve for PFS, Targeted arm",
  subtitle   = "Based on Kaplan-Meier estimates"
)
```

```{r}
surv_data$Time <- surv_data$Time/12
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods)
```

```{r}
GoF_PFS <- data.frame(AIC = fit_PFS$AIC, BIC = fit_PFS$BIC)
choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$AIC)]; choose_PFS
choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$BIC)]; choose_PFS
```

```{r}
mods=c("exp", "llogis")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods=mods)
```

```{r}
N_sim <- 100
fitted_PFS_targeted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline.RData")
```

### 2023-12-05 03_ancilliary-functions/Costs.R

@@ -5,62 +5,64 @@ gen_costs <- function(){
   # input:
   # output: a list with Inpatient_Costs.l , Outpatient_costs.l, AE_costs.l, Lookback_costs.l
   # see 06_report, Tables_out for source of values
+  inflat <- 151.2/133.4 # StatsCan CPI 2022 vs. 2018
+  discount <- 0 # x% discount, e.g. 20% discount = 0.2
   
-Inpatient_Costs.l <- list(
-  pre_prog = c(14955.52, 357.26),
-  prog_1 = c(3876.69, 806.4),
-  prog_2 = c(7358.42, 1367.02)) 
+  Inpatient_Costs.l  <- list(
+    pre_prog = c(14955.52, 357.26)*inflat, # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
+    prog_1   = c(3876.69, 806.4)  *inflat, # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
+    prog_2   = c(7358.42, 1367.02)*inflat) # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1) # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
   
-Outpatient_costs.l <- list(  pre_prog = c(3823.31),
-                             prog_1 = c(3786.90),
-                             prog_2 = c(3786.90))
-
-AE_cost.l <- list(Neurologic = c(30500,7400,1500),
-                  Auditory = c(8.33),
-                  Visual = c(17.95,8.98,5.98),
-                  Stroke = c(21735, 4933),
-                  Cardiac = c(20565,2997),
-                  SMN = c(4566.84,664.5))
-
-Lookback_cost.l  <- list(
-  death_plgg  =25960.21,
-  death_SN = 5494.93,
-  Dx_SN = 2842.71)
-
-
-General_pop_costs.l <- list(     five = 2383.36/12,
-                                 ten = 1412.68/12, 
-                                 fifteen = 1486.44/12, 
-                                 twenty = 1846.25/12, 
-                                 twentyfive = 1955.36/12, 
-                                 thirty = 2349.73/12, 
-                                 thirtyfive = 2618.95/12, 
-                                 fourty = 2543.75/12, 
-                                 fourtyfive = 2518.44/12, 
-                                 fifty = 2819.49/12, 
-                                 fiftyfive = 3281.00/12, 
[…]

### 2023-12-05 03_ancilliary-functions/Microsim.R

@@ -1,6 +1,6 @@
 Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_plgg,
                             Estimated_ae,AE_outside_mat,PrMortCardio_mat, SRS_mat1, cost_input,
-                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1 ){
+                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1, trt_duration ){
   # input:  
   # n.i: number of individuals
   # n.y: time horizon
@@ -13,6 +13,7 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
   # AE_outside_mat: output from AE_outside_pr
   # PrMortCardio_mat: output from MortCardio_est
   # SRS_mat1: output from SRS_gen
+  # trt_duration: 1 = lifetime; 2 = 2 years
   # output: 
   # list of model run outcomes with the same parameters but varying intervention
   
@@ -55,14 +56,14 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
   
   
   
-  for( intervention in c("Rad_Fused","Norad_Fused")){  
+  for( intervention in c("Targeted","SoC")){  
     
     # Assinging a logical to whether fused patients can be radiated  
-    if(intervention == "Rad_Fused"){
-      FusedNoRad <- FALSE
-    } else {
-      FusedNoRad <- TRUE
-    }
+    # if(intervention == "Rad_Fused"){
+    #   FusedNoRad <- FALSE
+    # } else {
+    #   FusedNoRad <- TRUE
+    # }
     
     # Reseeting radiation account
     
@@ -70,10 +71,12 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
     
     # 2. Initializing Values -----       
     #   m.Utilities (utilities) and m.Costs.plgg, m.Costs.ae
-    m.Utilities <- m.Costs.ae <-  m.Costs.plgg <- matrix(nrow = n.i, 
-                                                         ncol = n.t +1,
-                                                         dimnames = list(paste("ind", 1:n.i, sep = " "), 
-                                                                         paste( 0:n.t)),data = 0)
+    m.Utilities <- m.Costs.ae <-  m.Costs.plgg <- m.Costs.trt <- matrix(nrow = n.i, 
[…]

### 2023-12-05 03_ancilliary-functions/Probs.R

@@ -1,7 +1,7 @@
 # Probs.R
 
 Probs <- function( M_it, D_m,  df.i, Vis_m, CycleLength, GlobT, EstPLGG, EstAE,
-                   AE_outside_mat1,PrMortCardio_mat1,SRS_mat, curent_age_v,rad_benefit1){
+                   AE_outside_mat1,PrMortCardio_mat1,SRS_mat, curent_age_v, rad_benefit1, inter, tt, trt_dur){
   # input: 
   # M_it: a numeric vector indicating current state 
   # D_m: matrix (numeric) indicating the duration of stay in each state
@@ -49,21 +49,28 @@ Probs <- function( M_it, D_m,  df.i, Vis_m, CycleLength, GlobT, EstPLGG, EstAE,
   
   if(anyFused){
     # Use probs functions created earlier to estimate probabilities 
-    m.p.it[FusedLog, 1:4] <- Probs.plggFused(t_instate = plgg.timeinstate[FusedLog] +CycleLength , 
-                                             Cycle1 =  CycleLength,
-                                             StateIndx = plgg.char[FusedLog],FlexSurvRes = EstPLGG)
-    
-    # Similar for WT patients
-    m.p.it[!FusedLog,c(1,2,3,4)] <- Probs.plggWT(t_instate = plgg.timeinstate[!FusedLog] + CycleLength, 
-                                                 Cycle1 = CycleLength,
-                                                 StateIndx = plgg.char[!FusedLog],
-                                                 FlexSurvRes = EstPLGG)
+    # m.p.it[FusedLog, 1:4] <- Probs.plggFused(t_instate   = plgg.timeinstate[FusedLog] +CycleLength , 
+    #                                          Cycle1      =  CycleLength,
+    #                                          StateIndx   = plgg.char[FusedLog],
+    #                                          FlexSurvRes = EstPLGG,
+    #                                          inter       = inter,
+    #                                          tt          = tt,
+    #                                          trt_dur     = trt_dur)
+    # 
+    # # Similar for WT patients
+    # m.p.it[!FusedLog,c(1,2,3,4)] <- Probs.plggWT(t_instate = plgg.timeinstate[!FusedLog] + CycleLength, 
+    #                                              Cycle1 = CycleLength,
+    #                                              StateIndx = plgg.char[!FusedLog],
+    #                                              FlexSurvRes = EstPLGG)
     
   } else { # No fused
[…]

### 2023-12-05 03_ancilliary-functions/gen_synpop.R

@@ -1,6 +1,6 @@
 gen_synpop <- function( n1=  100000, deter = T){
   #l1: list of mean ,sd agedx, and neseted glms fit to fusion and sex
-    if(deter = T){
+    if(deter == T){
   AgeDx = round(runif(n = n1, min = 0,max = 18))
   coef1 <- c(0.03758116, -0.006658198) # intercenpt + AgeDx, binomial 
   o1 <- exp(cbind(1, AgeDx) %*% coef1)
@@ -8,8 +8,8 @@ gen_synpop <- function( n1=  100000, deter = T){
   coef2 <- c(0.1107713, -0.05921511, -0.2586516) # interept + Agedx + Sex
   
   o2 <- exp(cbind(1, AgeDx,Sex) %*% coef2)
-  Fusion =  rbinom(n1,1, prob = o2/(1+o2))
-  
+  #Fusion =  rbinom(n1,1, prob = o2/(1+o2))
+  Fusion <- rep(0, n1) # all WT (non-fused) patients
   
   ret<-  data.frame(AgeDx = AgeDx,
              Sex = Sex,

### 2023-12-05 03_ancilliary-functions/microsim-helpers.R

@@ -96,13 +96,21 @@ SurvProbFun <- function(object, t , cycle1){
 
 # rows 1,3,5,7,9 are associated with Fusion == 0
 
-Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes ){
+Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, trt_dur){
   # Inputs
   # t_instate: time in current state, a vector
   # StateIndx: what state are they in
   # Cycle1: cycle length
   # Outputs probability natrix
   # Probability matrix which i'll return
+  
+  if (inter == "Targeted") {
+    arm <- 2  
+  } else if (inter == "SoC") {
+    arm <- 11 
+  }
+  if (trt_dur == 2 & tt > 24) {arm <- 11} # treatment effect lasts for 2 years, goes back to SoC 
+  
   Prob.mat <-  matrix(nrow = length(t_instate), ncol = 4,data = 0)
   
   # If any state is equal to the first state uses the SurvProbFun 
@@ -111,8 +119,8 @@ Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes ){
 
   if(any(StateIndx ==  "pre_prog")){
     state1.log <- StateIndx ==  "pre_prog"
-    Prob.mat[state1.log,2] <- SurvProbFun(object = FlexSurvRes$flexobj[[1]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
-    Prob.mat[state1.log,4] <- SurvProbFun(object = FlexSurvRes$flexobj[[3]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
+    Prob.mat[state1.log,2] <- SurvProbFun(object = FlexSurvRes$flexobj[[arm]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
+    Prob.mat[state1.log,4] <- SurvProbFun(object = FlexSurvRes$flexobj[[3]][[1]],   t = t_instate[state1.log], cycle1 = Cycle1)
   }
   
   if(any(StateIndx ==   "prog1")){
@@ -130,25 +138,25 @@ Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes ){
 }
 
 # This is exact same structure as above only differencce is indexing in FlexSurvRes
[…]

### 2023-12-05 03_ancilliary-functions/summary.R

@@ -2,195 +2,293 @@
 
 # function of the following inputs
 sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
-                         costsplgg, costsAE, util, vRAD, vFusion  ){
-# What simulation number,
-# Parameter on radiation benefit
-# Intervention
-#sim_num = 1
-#intervention1 = "Intervention"
-#rr1 = 0
-# d_rate <- 0.00246627
-v_dwc <- 1 / (1 + d_rate) ^ (0:(dim(mM)[2]-1))   # calculate the cost discount weight based on the discount rate d.c 
-cyc_length <- 1/12
-max_age <- 80
-## Requires
-require(dplyr)
-require(stringr)
-
-
-
-# output
-
-res_ly <- vector(mode = "numeric", length = 3)
-type <-c("all","fused","fused_rad")
-
-## Matrix of model inputs
-# LY 
-#   All
-res_ly[[1]] <- mean(rowSums(util == 0)*cyc_length)
-#   Fused
-res_ly[[2]] <- mean(rowSums(util[vFusion == 1,] == 0)*cyc_length)
-#   Fused and Prog 1 
-res_ly[[3]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],] == 0)*cyc_length)
-
-df_LY <- tibble(Value = res_ly,  Variable = "LY", Type = "LY" ,  subset = type , discount = 0)
-
-res_qaly <- vector(mode = "numeric", length = 6)
-# QALY 
-#   All
-res_qaly[[1]] <- mean(rowSums(util*cyc_length*v_dwc))
-#   Fused
-res_qaly[[2]] <- mean(rowSums(util[vFusion == 1,]*cyc_length*v_dwc))
-#   Fused and Prog 1 
-res_qaly[[3]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],]*cyc_length*v_dwc))
-
-# QALY - undiscounted 
-#   All
-res_qaly[[4]] <- mean(rowSums(util*cyc_length))
-#   Fused
-res_qaly[[5]] <- mean(rowSums(util[vFusion == 1,]*cyc_length))
-#   Fused and Prog 1 
-res_qaly[[6]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],]*cyc_length))
-
-
-df_QALY <- tibble(Value = res_qaly, Variable = "QALY", Type = "QALY",
[…]

### 2023-12-05 04_analysis/Cost-effectiveness_basecase.R

@@ -103,11 +103,21 @@ dig_radbenefit1  <- readRDS(paste0(loc_here, "02_data/cherlow_dig.RDS"))
 
 k1 <- fun_genRadBenefit(dig_radbenefit =dig_radbenefit1, deter =T)
 
+## Survival curves
+# Targeted
+load(paste0(here::here("04_analysis","targeted survival"),"/fitted_PFS_targeted_swimmer.RData")) 
 
+# Control scenario 1
+load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk.RData")) 
+# Control scenario 2
+#load(paste0(here::here("04_analysis","control scenarios","Lianas paper PFS"),"/fitted_PFS_control_liana.RData")) 
+# Control scenario 3
+#load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk_firstline.RData")) 
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline.RData"))
 
 
 ## Global Parameters
-N_sim <- 1000
+N_sim <- 1
 torun1 <- 1:N_sim
 
 for(sim_num1 in torun1){
@@ -128,30 +138,49 @@ for(sim_num1 in torun1){
   # Estimating radiated paitents benefit
   
   # here stuck at generating flexsurv ojbects will be done after model run 
-  
-   rad_benefit_flex <- F
+  rad_benefit_flex    <- fun_genRadBenefit(dig_radbenefit = dig_radbenefit1, deter = F)
+  rad_benefit_flex$rr <- 1
+  #rad_benefit_flex <- F
   
   Estimated_plgg1 <- readRDS(
     paste0(loc_here,"02_data/bootstrap/bootstrapped_",sim_num1,"_TRUE.RDS"))
   Util_i <- gen_Effects(deter = F,  beta_Utils =df_beta_Utils)
   
+  # Bootstrap sampling with replacement from Liana's paper's PFS swimmer plot data
+  Estimated_plgg1$flexobj[[2]][1][[1]]  <- fitted_PFS_targeted[[sim_num1]] # Liana's paper's PFS (targeted)
+  Estimated_plgg1 <- rbind(Estimated_plgg1, Estimated_plgg1[1,])
[…]

### 2023-12-05 03_ancilliary-functions/Costs.R
Revert "updated to targeted first line"
This reverts commit f808ef81948c12109332a6e9a9ebff4e7debd4a8.

@@ -5,64 +5,62 @@ gen_costs <- function(){
   # input:
   # output: a list with Inpatient_Costs.l , Outpatient_costs.l, AE_costs.l, Lookback_costs.l
   # see 06_report, Tables_out for source of values
-  inflat <- 151.2/133.4 # StatsCan CPI 2022 vs. 2018
-  discount <- 0 # x% discount, e.g. 20% discount = 0.2
   
-  Inpatient_Costs.l  <- list(
-    pre_prog = c(14955.52, 357.26)*inflat, # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
-    prog_1   = c(3876.69, 806.4)  *inflat, # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
-    prog_2   = c(7358.42, 1367.02)*inflat) # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1) # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
+Inpatient_Costs.l <- list(
+  pre_prog = c(14955.52, 357.26),
+  prog_1 = c(3876.69, 806.4),
+  prog_2 = c(7358.42, 1367.02)) 
   
-  Outpatient_costs.l <- list(
-    pre_prog = c(3823.31)*inflat,  # Cycles 1-17 (Supp table 1)
-    prog_1   = c(3786.90)*inflat,  # Cycles 1 to 13 (0-52 weeks after progression) (Supp table 1)
-    prog_2   = c(3786.90)*inflat)  # Cycles 1 to 13 (0-52 weeks after progression) (Supp table 1)
-  
-  AE_cost.l <- list(Neurologic = c(30500,7400,1500)*inflat, # Cycle 1-2 post-injury; Cycles 3 to 11 after injury; Cycles 12 to (5 cycles before death) 
-                    Auditory   = c(8.33)*inflat,            # Cycle 1 to death
-                    Visual     = c(17.95,8.98,5.98)*inflat, # Cycles 1 to 12; Cycles 13 to 24; Cycles 25 to death
-                    Stroke     = c(21735, 4933)*inflat,     # Cycle 1; Cycles 2 to 20
-                    Cardiac    = c(20565,2997)*inflat,      # Cycle 1; Cycles 2 to 21
-                    SMN        = c(4566.84,664.5)*inflat)   # Cycles 1 - 6; Cycles 7- (12 cycles before death)
-  
[…]

### 2023-12-05 03_ancilliary-functions/Microsim.R

@@ -1,6 +1,6 @@
 Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_plgg,
                             Estimated_ae,AE_outside_mat,PrMortCardio_mat, SRS_mat1, cost_input,
-                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1, trt_duration ){
+                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1 ){
   # input:  
   # n.i: number of individuals
   # n.y: time horizon
@@ -13,7 +13,6 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
   # AE_outside_mat: output from AE_outside_pr
   # PrMortCardio_mat: output from MortCardio_est
   # SRS_mat1: output from SRS_gen
-  # trt_duration: 1 = lifetime; 2 = 2 years
   # output: 
   # list of model run outcomes with the same parameters but varying intervention
   
@@ -56,14 +55,14 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
   
   
   
-  for( intervention in c("Targeted","SoC")){  
+  for( intervention in c("Rad_Fused","Norad_Fused")){  
     
     # Assinging a logical to whether fused patients can be radiated  
-    # if(intervention == "Rad_Fused"){
-    #   FusedNoRad <- FALSE
-    # } else {
-    #   FusedNoRad <- TRUE
-    # }
+    if(intervention == "Rad_Fused"){
+      FusedNoRad <- FALSE
+    } else {
+      FusedNoRad <- TRUE
+    }
     
     # Reseeting radiation account
     
@@ -71,12 +70,10 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
     
     # 2. Initializing Values -----       
     #   m.Utilities (utilities) and m.Costs.plgg, m.Costs.ae
-    m.Utilities <- m.Costs.ae <-  m.Costs.plgg <- m.Costs.trt <- matrix(nrow = n.i, 
-                                                                        ncol = n.t +1,
-                                                                        dimnames = list(paste("ind", 1:n.i, sep = " "), 
-                                                                        paste( 0:n.t)),data = 0)
-    m.Costs.rad <- m.Costs.trt
-    
[…]

### 2023-12-05 03_ancilliary-functions/Probs.R

@@ -1,7 +1,7 @@
 # Probs.R
 
 Probs <- function( M_it, D_m,  df.i, Vis_m, CycleLength, GlobT, EstPLGG, EstAE,
-                   AE_outside_mat1,PrMortCardio_mat1,SRS_mat, curent_age_v, rad_benefit1, inter, tt, trt_dur){
+                   AE_outside_mat1,PrMortCardio_mat1,SRS_mat, curent_age_v,rad_benefit1){
   # input: 
   # M_it: a numeric vector indicating current state 
   # D_m: matrix (numeric) indicating the duration of stay in each state
@@ -49,28 +49,21 @@ Probs <- function( M_it, D_m,  df.i, Vis_m, CycleLength, GlobT, EstPLGG, EstAE,
   
   if(anyFused){
     # Use probs functions created earlier to estimate probabilities 
-    # m.p.it[FusedLog, 1:4] <- Probs.plggFused(t_instate   = plgg.timeinstate[FusedLog] +CycleLength , 
-    #                                          Cycle1      =  CycleLength,
-    #                                          StateIndx   = plgg.char[FusedLog],
-    #                                          FlexSurvRes = EstPLGG,
-    #                                          inter       = inter,
-    #                                          tt          = tt,
-    #                                          trt_dur     = trt_dur)
-    # 
-    # # Similar for WT patients
-    # m.p.it[!FusedLog,c(1,2,3,4)] <- Probs.plggWT(t_instate = plgg.timeinstate[!FusedLog] + CycleLength, 
-    #                                              Cycle1 = CycleLength,
-    #                                              StateIndx = plgg.char[!FusedLog],
-    #                                              FlexSurvRes = EstPLGG)
+    m.p.it[FusedLog, 1:4] <- Probs.plggFused(t_instate = plgg.timeinstate[FusedLog] +CycleLength , 
+                                             Cycle1 =  CycleLength,
+                                             StateIndx = plgg.char[FusedLog],FlexSurvRes = EstPLGG)
+    
+    # Similar for WT patients
+    m.p.it[!FusedLog,c(1,2,3,4)] <- Probs.plggWT(t_instate = plgg.timeinstate[!FusedLog] + CycleLength, 
+                                                 Cycle1 = CycleLength,
+                                                 StateIndx = plgg.char[!FusedLog],
+                                                 FlexSurvRes = EstPLGG)
     
   } else { # No fused
[…]

### 2023-12-05 03_ancilliary-functions/gen_synpop.R

@@ -1,6 +1,6 @@
 gen_synpop <- function( n1=  100000, deter = T){
   #l1: list of mean ,sd agedx, and neseted glms fit to fusion and sex
-    if(deter == T){
+    if(deter = T){
   AgeDx = round(runif(n = n1, min = 0,max = 18))
   coef1 <- c(0.03758116, -0.006658198) # intercenpt + AgeDx, binomial 
   o1 <- exp(cbind(1, AgeDx) %*% coef1)
@@ -8,8 +8,8 @@ gen_synpop <- function( n1=  100000, deter = T){
   coef2 <- c(0.1107713, -0.05921511, -0.2586516) # interept + Agedx + Sex
   
   o2 <- exp(cbind(1, AgeDx,Sex) %*% coef2)
-  #Fusion =  rbinom(n1,1, prob = o2/(1+o2))
-  Fusion <- rep(0, n1) # all WT (non-fused) patients
+  Fusion =  rbinom(n1,1, prob = o2/(1+o2))
+  
   
   ret<-  data.frame(AgeDx = AgeDx,
              Sex = Sex,

### 2023-12-05 03_ancilliary-functions/microsim-helpers.R

@@ -96,21 +96,13 @@ SurvProbFun <- function(object, t , cycle1){
 
 # rows 1,3,5,7,9 are associated with Fusion == 0
 
-Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, trt_dur){
+Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes ){
   # Inputs
   # t_instate: time in current state, a vector
   # StateIndx: what state are they in
   # Cycle1: cycle length
   # Outputs probability natrix
   # Probability matrix which i'll return
-  
-  if (inter == "Targeted") {
-    arm <- 2  
-  } else if (inter == "SoC") {
-    arm <- 11 
-  }
-  if (trt_dur == 2 & tt > 24) {arm <- 11} # treatment effect lasts for 2 years, goes back to SoC 
-  
   Prob.mat <-  matrix(nrow = length(t_instate), ncol = 4,data = 0)
   
   # If any state is equal to the first state uses the SurvProbFun 
@@ -119,8 +111,8 @@ Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, tr
 
   if(any(StateIndx ==  "pre_prog")){
     state1.log <- StateIndx ==  "pre_prog"
-    Prob.mat[state1.log,2] <- SurvProbFun(object = FlexSurvRes$flexobj[[arm]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
-    Prob.mat[state1.log,4] <- SurvProbFun(object = FlexSurvRes$flexobj[[3]][[1]],   t = t_instate[state1.log], cycle1 = Cycle1)
+    Prob.mat[state1.log,2] <- SurvProbFun(object = FlexSurvRes$flexobj[[1]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
+    Prob.mat[state1.log,4] <- SurvProbFun(object = FlexSurvRes$flexobj[[3]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
   }
   
   if(any(StateIndx ==   "prog1")){
@@ -138,25 +130,25 @@ Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, tr
 }
 
 # This is exact same structure as above only differencce is indexing in FlexSurvRes
[…]

### 2023-12-05 03_ancilliary-functions/summary.R

@@ -2,293 +2,195 @@
 
 # function of the following inputs
 sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
-                         costsplgg, costsAE, coststrt, costsrad, util, vRAD, vFusion  ){
-  # What simulation number,
-  # Parameter on radiation benefit
-  # Intervention
-  #sim_num = 1
-  #intervention1 = "Intervention"
-  #rr1 = 0
-  # d_rate <- 0.00246627
-  v_dwc <- 1 / (1 + d_rate) ^ (0:(dim(mM)[2]-1)) # calculate the cost discount weight based on the discount rate d.c 
-  ## Requires
-  require(dplyr)
-  require(stringr)
-  
-  # output
-  
-  res_ly <- vector(mode = "numeric", length = 3)
-  type   <- c("all","fused","fused_rad")
-  
-  ## Matrix of model inputs
-  # LY 
-  #   All
-  res_ly[[1]] <- mean(rowSums(util == 0)*cyc.t)
-  #   Fused
-  res_ly[[2]] <- mean(rowSums(util[vFusion == 1,] == 0)*cyc.t)
-  #   Fused and Prog 1 
-  res_ly[[3]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],] == 0)*cyc.t)
-  
-  df_LY       <- tibble(Value = res_ly,  Variable = "LY", Type = "LY" ,  subset = type , discount = 0)
-  
-  res_qaly    <- vector(mode = "numeric", length = 6)
-  
-  # QALY 
-  #   All
-  res_qaly[[1]] <- mean(rowSums(util*cyc.t*v_dwc))
-  #   Fused
-  res_qaly[[2]] <- mean(rowSums(util[vFusion == 1,]*cyc.t*v_dwc))
-  #   Fused and Prog 1 
-  res_qaly[[3]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],]*cyc.t*v_dwc))
-  
-  # QALY - undiscounted 
-  #   All
-  res_qaly[[4]] <- mean(rowSums(util*cyc.t))
-  #   Fused
-  res_qaly[[5]] <- mean(rowSums(util[vFusion == 1,]*cyc.t))
-  #   Fused and Prog 1 
-  res_qaly[[6]] <- mean(rowSums(util[vFusion == 1 & mVis[,2],]*cyc.t))
-  
-  df_QALY <- tibble(Value    = res_qaly, 
[…]

### 2023-12-05 04_analysis/Cost-effectiveness_basecase.R

@@ -103,21 +103,11 @@ dig_radbenefit1  <- readRDS(paste0(loc_here, "02_data/cherlow_dig.RDS"))
 
 k1 <- fun_genRadBenefit(dig_radbenefit =dig_radbenefit1, deter =T)
 
-## Survival curves
-# Targeted
-load(paste0(here::here("04_analysis","targeted survival"),"/fitted_PFS_targeted_swimmer.RData")) 
 
-# Control scenario 1
-load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk.RData")) 
-# Control scenario 2
-#load(paste0(here::here("04_analysis","control scenarios","Lianas paper PFS"),"/fitted_PFS_control_liana.RData")) 
-# Control scenario 3
-#load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk_firstline.RData")) 
-#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline.RData"))
 
 
 ## Global Parameters
-N_sim <- 1
+N_sim <- 1000
 torun1 <- 1:N_sim
 
 for(sim_num1 in torun1){
@@ -138,49 +128,30 @@ for(sim_num1 in torun1){
   # Estimating radiated paitents benefit
   
   # here stuck at generating flexsurv ojbects will be done after model run 
-  rad_benefit_flex    <- fun_genRadBenefit(dig_radbenefit = dig_radbenefit1, deter = F)
-  rad_benefit_flex$rr <- 1
-  #rad_benefit_flex <- F
+  
+   rad_benefit_flex <- F
   
   Estimated_plgg1 <- readRDS(
     paste0(loc_here,"02_data/bootstrap/bootstrapped_",sim_num1,"_TRUE.RDS"))
   Util_i <- gen_Effects(deter = F,  beta_Utils =df_beta_Utils)
   
-  # Bootstrap sampling with replacement from Liana's paper's PFS swimmer plot data
-  Estimated_plgg1$flexobj[[2]][1][[1]]  <- fitted_PFS_targeted[[sim_num1]] # Liana's paper's PFS (targeted)
-  Estimated_plgg1 <- rbind(Estimated_plgg1, Estimated_plgg1[1,])
[…]

### 2023-12-14 05_report/Manuscript_results_temp.Rmd
updated

---
title: "Manuscript results"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
#rm(list = ls())
```

```{r required packages}
require(tidyverse)    # for data manipulation
require(formattable)  # for formatting tables
require(knitr)        # for saving tables
require(scales)       # for ggplot axis labels
library(gridExtra)    # for gridded plots 
require(survival)     # for survival analysis
require(survminer)    # for survival plotting
```

compare survival curves (input and output)

time from 1st progression to model start (diagnosis to 1st prog or 1st prog to 2nd prog)

time to death

survival curves best/2nd best: choose the one that best reflects clinicians input (rather than AIC/BIC), use Exponential (force things to go down quicker, as clinicians don't expect the flattening)

discounting scenarios and 2nd-best distribution

## Data location

```{r}
#fileloc <- here::here("04_analysis","output","scenarios")
#fileloc <- "/Users/davidrios/OneDrive - SickKids/tomacbook"
```

The files are spread out over 5 folders.

## Table 2 & Abstract

Coding the following:

Table 2:Estimates of life-years after diagnosis, QALYs (Discounted) and Costs (Discounted) Estimates reported with 95% Confidence Interval in brackets. All costs are given in Canadian dollars.

Abstract results

```{R}
# model results 
#res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:10]
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount30", "/res_model"),full.names = TRUE)

#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_2yrs", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_2yrs_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_2yrs_discount30", "/res_model"),full.names = TRUE)

# turning into dataframe
df_model  <- map_df(res_model, readRDS) 
df_model <- df_model %>% filter(subset == "all")
# creating a key in the same format as the one in correct_surv
df_model <- df_model %>% 
  mutate(key = paste0(sim,"_",rr))

# fixing survival for everyone who doesn't have a correct survival time
df_model <- df_model %>% 
    mutate( Value = ifelse(Variable == "LY", 80-Value, Value))

# no longer need key 
df_model <- df_model %>%
  select(-key)
```

```{r}
df_output <- df_model %>% filter(discount == 1) %>% select(-rr)
# df_output$intervention[df_output$intervention == "SoC"] <- "Targeted"
df_output1 <- df_output %>% group_by(Variable, Type) %>% summarise(Mean = mean(Value))
write.csv(df_output1, "output.csv", row.names = F)
```

```{r}
df_delta <- df_model %>% 
  spread(intervention, Value) %>%   
  mutate(Delta = Targeted-SoC) %>% 
  select(-Targeted,-SoC)

df_model <- df_model %>% 
  group_by(Variable, Type, subset, intervention, discount, rr) %>% 
  summarise( mean = mean(Value),
             q025 = quantile(Value, 0.025),
             q975 = quantile(Value, 0.975)) %>% ungroup()
df_model <-df_model %>% 
  mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean,
                                                              symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(mean, 2))),
         q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q025, 2))),
        q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q975, 2))                  
                          )
         ) %>% 
  mutate( stat = paste0(mean, " (", q025, ";",q975,")"))

df_model1 <- df_model %>% 
  select(-mean, - q025, -q975)

df_delta1 <- df_delta %>% rename(Value = Delta) %>% 
  group_by(Variable, Type, subset, discount, rr) %>% 
  summarise( mean = mean(Value),
             q025 = quantile(Value, 0.025),
             q975 = quantile(Value, 0.975)) %>% ungroup() %>% 
  mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(mean, 2))),
         q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q025, 2))),
        q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q975, 2))

                          )
         ) %>% 
  mutate( stat = paste0(mean, " (", q025, ";",q975,")")) %>% 
    select(-mean, - q025, -q975)

df_deltacea <- df_delta %>% 
    filter(Type == "Total" | Type == "QALY", subset == "all", discount == 1 ) %>% select(-Type)  %>% spread(Variable, Delta)

df_model2 <- df_model1 %>% 
  bind_rows(mutate( df_delta1, intervention = "delta")) %>% 
    mutate(Variable = factor(Variable, levels = c("LY","QALY","Cost")),
         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE","Treatment","Radiation"))
         ) %>% 
  arrange(Variable, Type, discount, rr) %>% 
  spread(intervention, stat)

df_model3 <- df_model2 %>% 
  arrange(subset, rr, Variable, Type, discount )

tb2 <-df_model3  %>%
  filter(subset == "all") %>% 
  filter( !(Variable == "Cost" & discount == 0),
          !(Variable == "QALY" & discount == 0) ) %>%
  select(-Variable, - subset,-discount  ) %>% 
  rename(Variable = Type,
         Delta = delta,
         intervention = Targeted,
         control = SoC)

```

**Table 2**:

```{r}
library(pander)
library(forcats)

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  select(Variable, intervention, control, Delta , rr)

pander(tb2a)
```

## Supplementary Table 1

Supplementary Table 1: Estimates of life-years after diagnosis, QALYs (Discounted) and Costs (Discounted), for fused patients, and fused patients who progressed.

<!-- ```{r} -->

<!-- sm_tb1 <-df_model3  %>% -->
<!--   filter(subset == "fused") %>%  -->
<!--   filter( !(Variable == "Cost" & discount == 0), -->
<!--           !(Variable == "QALY" & discount == 0) ) %>% -->
<!--   select(-Variable,-discount  ) %>%  -->
<!--   rename(Variable = Type, -->
<!--          Delta = delta, -->
<!--          intervention = Targeted, -->
<!--          control = SoC)  -->

<!-- sm_tb1 <- sm_tb1 %>% rename(Control = control, -->
<!--                             Experimental = intervention, -->
<!--                             `Difference (Experimental - Control)` = Delta) -->
<!-- sm_tb1$Variable <- as.character(sm_tb1$Variable) -->
<!-- sm_tb1$Variable[3:7] <- c("Total costs", "Non-targeted therapy PLGG costs", "AE costs", -->
<!--                           "Treatment costs", "Radiation costs") -->

<!-- sm_tb1 %>% select(-subset, -rr) %>% select(Variable, Experimental, Control, `Difference (Experimental - Control)`) %>% -->
<!--   kable() -->
<!-- ``` -->

```{r}

```

<!-- ## Figure 4 Cost-effectiveness plane -->

<!-- Figure 4: Cost-effectiveness plane indicating the incremental cost and incremental effectiveness estimates related to molecular testing for each probabilistic simulation assuming both a no-radiation (n = 1,000) and radiation benefit (n = 1,000) -->

<!-- ```{r} -->
<!-- df_deltacea <- df_delta %>%  -->
<!--     filter(Type == "Total" | Type == "QALY", subset == "fused", discount == 1 ) %>% select(-Type)  %>% spread(Variable, Delta) -->

<!-- df_deltacea1 <- df_deltacea %>%  -->
<!--   mutate(rr =factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit")), -->
<!--          type = "all") -->
<!-- df_means <- df_deltacea %>%  -->
<!--   group_by(rr) %>%  -->
<!--   summarise(Cost = mean(Cost), -->
<!--             QALY = mean(QALY)) %>%  -->
<!--   mutate(type = "Mean Values") %>%  -->
<!--   mutate(rr1 = factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit") )) -->
<!-- toplot_plane <-df_deltacea1 %>%  -->
<!--   ggplot() +  -->
<!--   geom_point(aes(x = QALY, y = Cost), alpha = 0.75 , size = 0.6) +  -->
<!--   # geom_point(aes(x = QALY, y = Cost), color = "black", data = df_means,shape = 2,show.legend = TRUE, size = 3) +  -->
<!--   geom_hline(yintercept = 0) +  -->
<!--   geom_vline(xintercept = 0) +  -->
<!--   theme_bw() +  -->
<!--   theme(legend.title = element_blank()) + -->
<!--   ylab("Discounted Total Costs") +   -->
<!--   xlab("Discounted QALYs") +  -->
<!--   labs(color = "", shape = "Mean") + -->
<!--   scale_y_continuous(labels = dollar_format(prefix="$")) + -->
<!--   facet_wrap(~ rr) +  -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- toplot_plane -->

<!-- ``` -->

<!-- # Figure 2  -->

<!-- Figure 2: Median cumulative incidence of all-cause mortality for all patients assuming n o radiation benefit or with radiation benefit. -->

<!-- ```{r} -->
<!-- res_os <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE) -->
<!-- df_OS <- map_df(res_os, readRDS) -->

<!-- df_med <- df_OS %>% -->
<!--   group_by(cycle, type, intervention, rr) %>% -->
<!--   summarise(median = median(OS)) %>% ungroup() %>% -->
<!--    mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) %>% -->
<!--     mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control")) -->

<!-- df_delta <- df_OS %>% -->
<!--   spread(intervention, OS) %>% -->
<!--   mutate(delta = (1-Targeted) - (1-SoC)) %>% -->
<!--   select(-Targeted, - SoC) %>% -->
<!--   group_by(cycle, type, rr) %>% -->
<!--   summarise(median = median(delta), -->
<!--             q025 = quantile(delta, 0.025), -->
<!--             q975 = quantile(delta, 0.975)) %>% ungroup() %>%  -->
<!--   mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) -->

<!-- rm(df_OS) -->

<!-- plot1 <- filter(df_med,type == "OS") %>% -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = cycle, y = 1-median, linetype = intervention)) + -->
<!--   facet_wrap(~rr) + -->
<!--   theme_bw() +  -->
<!--   ylab("\n Cumulative Incidence, all-cause mortality") +  -->
<!--   xlab("Time from diagnosis, Years")  +  -->
<!--     theme(legend.title =element_blank(),legend.position="top") + -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- plot2_delta <- filter(df_delta,type == "OS" ) %>% -->
<!--   mutate(t1 = "Median (95% CI)") %>%  -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = cycle, y = median, color = t1)) +  -->
<!--   geom_ribbon(aes(x = cycle, ymin = q025, ymax = q975, fill = t1), alpha = 0.3,show.legend = T) + -->
<!--   facet_wrap(~rr) + theme_bw() + -->
<!--   ylab("Delta (Intervention - Control) \n Cumulative Incidence, all-cause mortality") +  -->
<!--     xlab("Time from diagnosis, Years") +  -->
<!--   theme(legend.title =element_blank(),legend.position="top")  + -->
<!--   scale_color_manual(values = "black") + -->
<!--   scale_fill_manual( values = "black") + -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- fig2 <-grid.arrange(plot1, plot2_delta) -->

<!-- fig2 -->
<!-- ``` -->

<!-- In text results -->

<!-- ```{r} -->
<!-- df_med %>%  -->
<!--   filter(cycle == 20) %>% mutate(median = median*100) %>%  -->
<!--   spread(intervention, median) %>%  -->
<!--   arrange(rr, type) %>% filter(type == "OS" | type == "Fused") %>%   -->
<!--   kable(digits = 1 )  -->
<!-- ``` -->

<!-- # Supp Fig 1 -->

<!-- Supplementary Figure 1: Cumulative incidence of all-cause mortality for all fused patients, and for fused patients who progressed -->

<!-- ```{r} -->
<!-- plot2SM <-filter(df_delta,type != "OS" ) %>% -->
<!--   mutate(type = factor(type, levels = c("Fused","FusedProg"), -->
<!--                        labels = c("Fused patients", "Fused patients that progressed"))) %>%  -->
<!--  mutate(t1 = "Median (95% CI)") %>%  -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = cycle, y = median, color = t1)) +  -->
<!--   geom_ribbon(aes(x = cycle, ymin = q025, ymax = q975, fill = t1), alpha = 0.3,show.legend = T) + -->
<!--   facet_wrap(~rr + type,) + theme_bw() + -->
<!--   ylab("Delta (Intervention - Control) \n Cumulative Incidence, all-cause mortality") +  -->
<!--     xlab("Time from diagnosis, Years") +  -->
<!--   theme(legend.title =element_blank(),legend.position="top")  + -->
<!--   scale_color_manual(values = "black") + -->
<!--   scale_fill_manual( values = "black")  + -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- plot2SM -->

<!-- rm(fig2) -->
<!-- ``` -->

<!-- ## Figure 3  -->

<!-- Create figure 3  -->

<!-- First accounting for mortality  -->

<!-- ```{r eval=T, message=FALSE, warning=FALSE, include=FALSE} -->
<!-- res_CI <- list.files(paste0(fileloc, "/res_CI"),full.names = TRUE) -->
<!-- res_OS <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE) -->

<!-- res_CI_s <- list.files(paste0(fileloc, "/res_CI"),full.names = FALSE) -->
<!-- res_OS_s <- list.files(paste0(fileloc, "/res_OS"),full.names = FALSE) -->

<!-- res_OS <- res_OS[order(res_OS_s)] -->
<!-- res_CI <- res_CI[order(res_CI_s)] -->

<!-- res_short <- list.files(paste0(fileloc, "/res_CI"),full.names = F) -->
<!-- res_short <- res_short[order(res_OS_s)] -->
<!-- v_n <-c( "neurologic", "auditory", "visual", "stroke", "cardiovascular", "SN") -->

<!-- ## first read in first thing  -->

<!-- for( i in seq_along(res_short)){ -->
<!--   if(i %% 10 == 0){message(i/length(res_short))} -->
<!-- tempCI <- readRDS(res_CI[i]) -->
<!-- tempOS <- readRDS(res_OS[i]) %>% rename(time = cycle) %>% filter(type == "OS") -->
<!-- tempOS <-tempOS %>% group_by(type, sim , intervention, rr) %>%  -->
<!--   mutate(OS_t1 = lag(OS, 1,1)) %>%  -->
<!--   select(-type) -->

<!-- tempCI <- tempCI %>%  -->
<!--   left_join(tempOS, by = c("time", "sim", "intervention", "rr")) -->

<!-- calcCI <- tempCI %>%  -->
<!--   filter(state %in% v_n) %>% -->
<!--     mutate(ci = (ceiling(ci*100000)*ceiling(OS*100000))/100000) %>%  -->
<!--     mutate(ci = ceiling(ci*100000), -->
<!--            OS = ceiling(OS*100000), -->
<!--            OS_t1= ceiling(OS_t1*100000)/100000) %>% -->
<!--   group_by(state, intervention, rr ) %>% -->
<!--   mutate(ci = c(0,diff(ci,1))) %>%  -->
<!--   mutate(mcf =  ci/OS, -->
<!--          CI = mcf*OS_t1 -->
<!--          ) %>%  -->
<!--   mutate(cumCI = cumsum(CI))  %>% -->
<!--   select(state, intervention ,rr, time,cumCI, sim ) %>% ungroup() -->

<!-- for(state1 in v_n){ -->
<!--   dir.create(path = here::here("05_report","1newCIcalc",state1),recursive = T) -->

<!--      filter(calcCI, state == state1) %>% -->
<!--       saveRDS(file = here::here("05_report","1newCIcalc",state1,"/",paste0(state1,i,"BIG.RDS"))) -->

<!-- } -->

<!-- } -->

<!-- ``` -->

<!-- ```{r} -->
<!-- store_toplot <- vector(mode = "list", length = length(v_n)) -->

<!-- for(j in seq_along(v_n)){ -->
<!--   message(j) -->

<!--   list_files_instate <- list.files(here::here("05_report","1newCIcalc",v_n[j]),full.names = TRUE) -->

<!-- big1   <- map_df(list_files_instate, readRDS) -->

<!-- store_toplot[[j]] <- big1 %>%  -->
<!--   group_by(intervention, state,rr) %>% -->
<!--   group_by(intervention, state,rr) %>% -->
<!--   mutate(cumCI = ifelse(is.nan(cumCI) , NA, cumCI  )) %>% -->
<!--   fill(cumCI,.direction = "down") %>% -->
<!--   group_by(intervention, state, rr,  time  ) %>% -->
<!-- summarise(median = median(cumCI), -->
<!--           q025 = quantile(cumCI, 0.025), -->
<!--           q975 = quantile(cumCI, 0.975)) %>% ungroup() -->

<!-- } -->

<!-- unlink(here::here("05_report","1newCIcalc"),recursive = T) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- toplotCI <- do.call(rbind,store_toplot) -->

<!-- plotCI <- toplotCI %>% ungroup() %>% -->
<!--     mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control")) %>%  -->
<!--     mutate(rr= ifelse(rr == 1, "Cherlow, et al.","No radiation benefit")) %>% -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = time, y = median, color = intervention)) +   geom_ribbon(aes(x = time, ymin = q025, ymax = q975 , fill = intervention), alpha = 0.3,show.legend = T) + -->
<!--  facet_grid(rows =  vars(state) , cols =  vars(rr) ) + -->
<!-- theme_bw() + -->
<!--   ylab("Cumulative incidence, Treatment related AE") +  -->
<!--     xlab("Time from diagnosis, Years") +  -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- plotCI -->
<!-- ``` -->

<!-- ```{r} -->

<!-- dir.create(here::here("05_report","tempfold1")) -->
<!-- res_CI <- list.files(paste0(fileloc, "/res_CI"),full.names = TRUE) -->
<!-- res_OS <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE) -->

<!-- res_CI_s <- list.files(paste0(fileloc, "/res_CI"),full.names = FALSE) -->
<!-- res_OS_s <- list.files(paste0(fileloc, "/res_OS"),full.names = FALSE) -->

<!-- res_OS <- res_OS[order(res_OS_s)] -->
<!-- res_CI <- res_CI[order(res_CI_s)] -->

<!-- res_short <- list.files(paste0(fileloc, "/res_CI"),full.names = F) -->
<!-- res_short <- res_short[order(res_OS_s)]  -->

<!-- list1 <- c("stroke_gen","cardiovascular_gen","SN_gen") -->
<!-- list2 <- c("stroke","cardiovascular","SN") -->
<!-- v_n <- c(list1,list2) -->

<!-- ## first read in first thing  -->

<!-- for( i in 1:length(res_short)){ -->
<!--   if(i %% 10 == 0){message(i/length(res_short))}  -->
<!--   tempCI <- readRDS(res_CI[i])  -->
<!--   tempOS <- readRDS(res_OS[i]) %>%  -->
<!--     rename(time = cycle) %>% filter(type == "OS") -->

<!--   tempOS <-tempOS %>% group_by(type, sim , intervention, rr) %>% -->
<!--   mutate(OS_t1 = lag(OS, 1,1)) %>% -->
<!--   select(-type) -->

<!-- tempCI <- tempCI %>% -->
<!--   left_join(tempOS, by = c("time", "sim", "intervention", "rr")) -->

<!-- ## Have TempCI joined with tempOS -->
<!-- ## issue is that i calcualted CI = cumsum(mean(incidence*OS)) ##  mean(abs(mDur1[,ci_states[j]] - time_v[t1]) < tol)/per_alive[t1] ## cumsum(k1) ## Reversing that -->

<!-- calCI <-tempCI %>% -->
<!--   filter(state %in% v_n) %>% -->
<!--   group_by(state, sim, intervention ,rr, type) %>%arrange(time) %>% -->
<!--   mutate(i = c(0, diff(ci)), -->
<!--          i = (i*100000)*OS, -->
<!--          ) %>% ungroup() %>% -->
<!--   mutate(state = case_when( -->
<!-- state == list1[1] |state ==  list2[1] ~ list2[1], state == list1[2] |state ==  list2[2] ~ list2[2], state == list1[3] |state ==  list2[3] ~ list2[3] -->
<!-- )) %>%  -->
<!--    group_by(state, sim, intervention ,rr, type, time) %>% -->
<!--   mutate( i = sum(i)) %>%  ungroup() %>%  -->
<!--    group_by(state, sim, intervention ,rr, type) %>% -->
<!--    mutate(mcf =  i /(OS*100000), -->
<!--          CI = mcf*OS_t1 -->
<!--          )  %>%  -->
<!--     mutate(cumCI = cumsum(CI))  %>% -->
<!--   select(state, intervention ,rr, time,cumCI, sim, type )  -->

<!-- # trying to fix that cumulative incidence doesnt take into account mortality  -->

<!--       saveRDS(file = here::here("05_report","tempfold1",paste0(i,"BIG.RDS")),object = calCI)  -->
<!--       }  -->
<!-- ``` -->

<!-- ```{r} -->

<!-- file1 <- list.files(here::here("05_report","tempfold1"),full.names = T) -->

<!-- bigdf<-map_df(file1, readRDS) -->

<!-- bigdf %>% arrange(desc(cumCI)) -->

<!-- bigdf %>%  -->
<!--    mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) %>% -->
<!--     mutate(intervention  = ifelse(intervention == "Targeted", "Intervention","Control")) %>% -->
<!--   group_by(state, intervention, rr, time,type) %>%  -->
<!--   summarise(mean = mean(cumCI), -->
<!--             q025 = quantile(cumCI,0.025), -->
<!--             q975 = quantile(cumCI,0.975)) %>%  -->

<!--   ggplot() + -->
<!--   facet_wrap(~state+ rr) + geom_line(aes(x = time, y= mean, color = intervention)) + -->
<!--   geom_ribbon(aes(x = time, ymin = q025, ymax = q975, fill = intervention), alpha = 0.1)+ -->
<!--   theme_bw() -->

<!-- unlink(here::here("05_report","tempfold1"),recursive = T) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- icd_10_death <- c("O95", "O96", "O97", "R96", "R97", "R98", "R99") -->
<!-- Df_full$icd_death <- rep(0, nrow(Df_full)) -->
<!-- for (i in 1:nrow(Df_full)) { -->
<!--   if (substr(Df_full$DIAG_CODE_1[i], 1, 3) %in% icd_10_death |  -->
<!--       substr(Df_full$DIAG_CODE_2[i], 1, 3) %in% icd_10_death | -->
<!--       substr(Df_full$DIAG_CODE_3[i], 1, 3) %in% icd_10_death | -->
<!--       substr(Df_full$DIAG_CODE_4[i], 1, 3) %in% icd_10_death | -->
<!--       substr(Df_full$DIAG_CODE_5[i], 1, 3) %in% icd_10_death ) { -->
<!--     Df_full$icd_death[i] <- 1 -->
<!--   }  -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- icd_10_death <- c("O95", "O96", "O97", "R96", "R97", "R98", "R99") -->
<!-- Df_full %>% select(substr(Df_full$DIAG_CODE_1[i], 1, 3) %in% icd_10_death |  -->
<!--                    substr(Df_full$DIAG_CODE_2[i], 1, 3) %in% icd_10_death | -->
<!--                    substr(Df_full$DIAG_CODE_3[i], 1, 3) %in% icd_10_death | -->
<!--                    substr(Df_full$DIAG_CODE_4[i], 1, 3) %in% icd_10_death | -->
<!--                    substr(Df_full$DIAG_CODE_5[i], 1, 3) %in% icd_10_death) -->
<!-- ``` -->

### 2023-12-14 03_ancilliary-functions/microsim-helpers.R

@@ -136,6 +136,9 @@ Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, tr
   
   return(Prob.mat)
 }
+# Estimated_plgg1$flexobj[[5]][[1]] -> prog1to2
+# prog1to2$res[,1] -> res2
+# plot(0:10,plnorm(0:10, meanlog=res2[1], sdlog=res2[2], lower.tail = F), ylim=c(0,1), type="l")
 
 # This is exact same structure as above only differencce is indexing in FlexSurvRes
 # Probs.plggFused <- function(t_instate,StateIndx, Cycle1,FlexSurvRes ){

### 2023-12-14 04_analysis/Cost-effectiveness_basecase.R

@@ -105,21 +105,17 @@ k1 <- fun_genRadBenefit(dig_radbenefit =dig_radbenefit1, deter =T)
 
 ## Survival curves
 # Targeted
-load(paste0(here::here("04_analysis","targeted survival"),"/fitted_PFS_targeted_swimmer.RData")) 
+load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline.RData"))
 
-# Control scenario 1
-load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk.RData")) 
-# Control scenario 2
-#load(paste0(here::here("04_analysis","control scenarios","Lianas paper PFS"),"/fitted_PFS_control_liana.RData")) 
-# Control scenario 3
-#load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk_firstline.RData")) 
-#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline.RData"))
-
+# Control 
+load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline.RData"))
+# load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk_firstline.RData"))
 
 ## Global Parameters
-N_sim <- 1
+N_sim <- 10
 torun1 <- 1:N_sim
 
+start.time <- Sys.time()
 for(sim_num1 in torun1){
   
   sim_num <- sim_num1
@@ -147,12 +143,12 @@ for(sim_num1 in torun1){
   Util_i <- gen_Effects(deter = F,  beta_Utils =df_beta_Utils)
   
   # Bootstrap sampling with replacement from Liana's paper's PFS swimmer plot data
-  Estimated_plgg1$flexobj[[2]][1][[1]]  <- fitted_PFS_targeted[[sim_num1]] # Liana's paper's PFS (targeted)
+  Estimated_plgg1$flexobj[[2]][1][[1]]  <- fitted_PFS_targeted[[sim_num1]] # Eric's paper's PFS (targeted)
   Estimated_plgg1 <- rbind(Estimated_plgg1, Estimated_plgg1[1,])
-  Estimated_plgg1$flexobj[[11]][1][[1]] <- fitted_PFS_chemo[[sim_num1]]    # Sickkids/Bryan data PFS (control)
[…]

### 2024-02-05 04_analysis/control scenarios/Bryans SickKids data firstline/chart_audit_survival_new_controls_firstline.Rmd
upload results combo prices

--- 2023-12-05 04_analysis/control scenarios/Bryans SickKids data/chart_audit_survival_new_controls_firstline.Rmd
@@
   pval       = F,                # Add p-value
-  risk.table = F,                # Add risk table
+  risk.table = T,                # Add risk table
   risk.table.height = 0.25,      # Useful to change when you have multiple groups
@@
   xlab       = 'Time in years', # Change X-axis label
-  title      = "Survival curve for PFS",
-  subtitle   = "Based on Kaplan-Meier estimates"
+  title      = "Kaplan-Meier survival curve for PFS, Control arm",
+  subtitle   = "Source: SickKids (first-line)"
 )
@@
 }
-save(fitted_PFS_chemo, file="fitted_PFS_control_sk_firstline.RData")
+save(fitted_PFS_chemo, file="fitted_PFS_control_sk_firstline_exp_100.RData")
 ```

### 2024-02-05 04_analysis/control scenarios/Bryans SickKids data/chart_audit_survival_new_controls.Rmd
upload results combo prices

---
title: "Survival Analysis Chart Audit Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(survival)
library(flexsurv)
library(survminer)
library(here)
library(darthtools)
library(data.table)
```

- date last FU CCO gone
- age_diag same as age_diag_years

```{r}
loc_here <- getwd()
# df0 <- read_csv(paste0(loc_here, "02_data/PLGG_targeted_chartaudit_form.csv"), skip=1)
# df <- read_csv("plgg_cea_controls.csv")
df <- read_csv("PLGG_CEA_ChemoORRad_Control_Oct2023.csv")
df$status <- ifelse(df$secondprogression  == 1 | df$death == 1, 1 ,0)
df$time <- df$TimetoOutcome_from1stprogression_days/365 # change time in days to in years
```

Kaplan-Meier estimates of PFS

```{r}
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = status) ~ 1, data = df)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = df,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in years', # Change X-axis label
  title      = "Kaplan-Meier survival curve for PFS, Both arms",
  subtitle   = "Source: SickKids"
)
```

# Fit survival curves:

*Control arm:*

```{r}
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gengamma", "rps")
fit_control <- fit.fun(time="time", status="status", mods=mods, 
                       data=df %>% as.data.frame(), extrapolate = T, times=times) 
a <- fit_control$plot
a$plot <- a$plot + labs(subtitle="Control arm (n=18)") + scale_x_continuous(breaks=seq(0,80,10))
a$plot
```

Choose best-fitting survival model:

```{r}
GoF_control <- data.frame(AIC = fit_control$AIC, BIC = fit_control$BIC)
choose_PFS_AIC_control <- rownames(GoF_control)[which.min(GoF_control$AIC)]; choose_PFS_AIC_control
choose_PFS_BIC_control <- rownames(GoF_control)[which.min(GoF_control$BIC)]; choose_PFS_BIC_control
```

```{r}
mods <- c("lnorm", "exp")
fit_control <- fit.fun(time="time", status="status", mods=mods, 
                       data=df %>% as.data.frame(), extrapolate = T, times=times) 
a1 <- fit_control$plot
a1$plot <- a1$plot + labs(subtitle="Control arm (n=18), best-fitting curve") + 
  scale_x_continuous(breaks=seq(0,80,10))
a1$plot
```

Calculate transition probabilities (prog 1 to prog 2):

```{r}
best_model_control <- fit_control$model.objects$models$Exponential
surv_probs_control <- surv_prob(best_model_control, times = times) # surv probs (not having 2nd prog) from prog 1
trans_probs_control <- trans_prob(surv_probs_control) # transition probs from prog 1 to prog 2
```

Bootstrap for microsim:

```{r}
N_sim <- 100
fitted_PFS_chemo_sk <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(df), replace=T)
  PFS_data_boot <- df[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "status", 
                     data = PFS_data_boot %>% as.data.frame(),
                     extrapolate = T, times=times, mods=c("exp"))
  fitted_PFS_chemo_sk[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_chemo_sk, file="fitted_PFS_control_sk_exp_100.RData")
```

```{r}

```

<!-- # Mortality -->

<!-- ```{r} -->
<!-- loc_here <- getwd() -->
<!-- # df0 <- read_csv(paste0(loc_here, "02_data/PLGG_targeted_chartaudit_form.csv"), skip=1) -->
<!-- # df <- read_csv("plgg_cea_controls.csv") -->
<!-- df <- read_csv("PLGG_CEA_ChemoORRad_Control_Oct2023.csv") -->
<!-- df$status <- ifelse(df$death == 1, 1 ,0) -->
<!-- df$time <- df$TimetoOutcome_from1stprogression_days/365 # change time in days to in years -->
<!-- ``` -->

<!-- Kaplan-Meier estimates of PFS -->

<!-- ```{r} -->
<!-- # Kaplan-Meier fit for PFS -->
<!-- KM_PFS <- survfit(Surv(time = time, event = status) ~ 1, data = df) -->
<!-- # plot KM for PFS -->
<!-- ggsurvplot( -->
<!--   KM_PFS, -->
<!--   data       = df, -->
<!--   size       = 1,                # change line size -->
<!--   conf.int   = FALSE,            # Add confidence interval -->
<!--   pval       = F,                # Add p-value -->
<!--   risk.table = F,                # Add risk table -->
<!--   risk.table.height = 0.25,      # Useful to change when you have multiple groups -->
<!--   ggtheme    = theme_bw(),       # Change ggplot2 theme -->
<!--   xlab       = 'Time in years', # Change X-axis label -->
<!--   title      = "Survival curve for PFS", -->
<!--   subtitle   = "Based on Kaplan-Meier estimates" -->
<!-- ) -->
<!-- ``` -->

<!-- # Fit survival curves: -->

<!-- *Control arm:* -->

<!-- ```{r} -->
<!-- times <- 0:80 -->
<!-- mods <- c("exp", "weibull", "gamma", "llogis", "rps") -->
<!-- fit_control <- fit.fun(time="time", status="status", mods=mods,  -->
<!--                        data=df %>% as.data.frame(), extrapolate = T, times=times)  -->
<!-- a <- fit_control$plot -->
<!-- a$plot <- a$plot + labs(subtitle="Control arm (n=18)") + scale_x_continuous(breaks=seq(0,80,10)) -->
<!-- a$plot -->
<!-- ``` -->

<!-- Choose best-fitting survival model: -->

<!-- ```{r} -->
<!-- GoF_control <- data.frame(AIC = fit_control$AIC, BIC = fit_control$BIC) -->
<!-- choose_PFS_AIC_control <- rownames(GoF_control)[which.min(GoF_control$AIC)]; choose_PFS_AIC_control -->
<!-- choose_PFS_BIC_control <- rownames(GoF_control)[which.min(GoF_control$BIC)]; choose_PFS_BIC_control -->
<!-- ``` -->

<!-- ```{r} -->
<!-- mods <- c("exp") -->
<!-- fit_control <- fit.fun(time="time", status="status", mods=mods,  -->
<!--                        data=df %>% as.data.frame(), extrapolate = T, times=times)  -->
<!-- a1 <- fit_control$plot -->
<!-- a1$plot <- a1$plot + labs(subtitle="Control arm (n=18), best-fitting curve") +  -->
<!--   scale_x_continuous(breaks=seq(0,80,10)) -->
<!-- a1$plot -->
<!-- ``` -->

<!-- Calculate transition probabilities (prog 1 to prog 2): -->

<!-- ```{r} -->
<!-- best_model_control <- fit_control$model.objects$models$Exponential -->
<!-- surv_probs_control <- surv_prob(best_model_control, times = times) # surv probs (not having 2nd prog) from prog 1 -->
<!-- trans_probs_control <- trans_prob(surv_probs_control) # transition probs from prog 1 to prog 2 -->
<!-- ``` -->

<!-- Bootstrap for microsim: -->

```{r}
# N_sim <- 100
# fitted_PFS_death <- list()
# set.seed(1)
# for (i in 1:N_sim) {
#   ids <- sample(1:nrow(df), replace=T)
#   PFS_data_boot <- df[ids,]
#   fit_PFS <- fit.fun(time  = "time", status = "status",
#                      data = PFS_data_boot %>% as.data.frame(),
#                      extrapolate = T, times=times, mods=c("exp"))
#   fitted_PFS_death[[i]] <- fit_PFS$model.objects$models$Exponential
#   print(i)
# }
# save(fitted_PFS_death, file="fitted_PFS_death_sk.RData")
```

### 2024-02-05 04_analysis/control scenarios/Erics firstline RCT/first_line_paper_survival.Rmd
updated
upload results combo prices

@@
 
-# 04 Digitized Data
+# Independent Reviewer
+
+## 04 Digitized Data
 
@@
   xlab       = 'Time in months', # Change X-axis label
-  title      = "Survival curve for PFS, Control arm",
-  subtitle   = "Based on Kaplan-Meier estimates"
+  title      = "Kaplan-Meier survival curve for PFS, Control arm (Independent Reviewer)",
+  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
 )
@@
 ```{r}
-surv_data$Time <- surv_data$Time/12 # change time in months to years
+# surv_data$Time <- surv_data$Time/12 # change time in months to years
+IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
 # times <- seq(0,5,by=1/12)
@@
 }
-save(fitted_PFS_chemo, file="fitted_PFS_control_firstline.RData")
+save(fitted_PFS_chemo, file="fitted_PFS_control_firstline_lnorm_100.RData")
 ```
@@
   xlab       = 'Time in months', # Change X-axis label
-  title      = "Survival curve for PFS, Targeted arm",
-  subtitle   = "Based on Kaplan-Meier estimates"
+title      = "Kaplan-Meier survival curve for PFS, Targeted arm (Independent Reviewer)",
+  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
 )
@@
 ```{r}
-surv_data$Time <- surv_data$Time/12
+IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
 # times <- seq(0,5,by=1/12)
@@
 ```{r}
-mods=c("exp", "llogis")
+mods=c("exp", "lnorm")
 fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
@@
 }
-save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline.RData")
+save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_exp_100.RData")
 ```
+
+```{r}
+N_sim <- 100
+fitted_PFS_targeted <- list()
+set.seed(1)
+for (i in 1:N_sim) {
+  ids <- sample(1:nrow(IPD_PFS), replace=T)
+  PFS_data_boot <- IPD_PFS[ids,]
+  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
+                     times = times, extrapolate = T, mods=c("lnorm"))
+  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$`log-Normal`
+  print(i)
+}
+save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_lnorm_100.RData")
+```
+
+# Investigator Assessment
+
+## 04 Digitized Data
+
+Use the function `digitise()` to translate the digitised OS and PFS data into patient level information.
+
+## Control arm
+
+```{r}
+time_interval <- seq(0, 36, by = 2)
+at_risk <- c(37,28,22,22,16,14,13,11,11,11,6,6,4,3,2,1,0,0,0)
+surv_data <- read.csv("Eric NEJM investigator digitized.csv", header = T)
+surv_data <- surv_data[surv_data$curve==1,]
+surv_data$St <- surv_data$St/100
+surv_data <- data.frame(k = 1:nrow(surv_data),
+                        Time = surv_data$time,
+                        Sk = surv_data$St)
+write.table(surv_data, file = "first_line_PFS_curve_control_investigator.txt", row.names = F)
+surv_data <- read.table("first_line_PFS_curve_control_investigator.txt", header = T)
+surv_times <- surv_data$Time
+
+n_risk_table <- create_at_risk_table(survival_time = surv_times,
+                                     Years = time_interval,
+                                     AtRisk = at_risk)
+write.table(n_risk_table, "first_line_PFS_risktable_control_investigator.txt", row.names = F)
+```
+
+```{r, results="hide"}
+# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
+digitise(surv_inp   = "first_line_PFS_curve_control_investigator.txt", 
+         nrisk_inp  = "first_line_PFS_risktable_control_investigator.txt", 
+         km_output  = "first_line_PFS_KM_control_investigator.txt", 
+         ipd_output = "first_line_PFS_IPD_control_investigator.txt")
+
+# Link the IPD files across the two arms of the trial for OS and PFS
+IPD_PFS <- make.ipd(ipd_files = c("first_line_PFS_IPD_control_investigator.txt"), ctr = 1,
+                    var.labs  = c("time","event","arm"))
+IPD_PFS <- IPD_PFS %>% select(-arm)
+```
+
+```{r}
+library(survival)
+library(survminer)
+# Kaplan-Meier fit for PFS
+KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
+# plot KM for PFS
+ggsurvplot(
+  KM_PFS,
+  data       = IPD_PFS,
+  size       = 1,                # change line size
+  conf.int   = FALSE,            # Add confidence interval
+  pval       = F,                # Add p-value
+  risk.table = T,                # Add risk table
+  risk.table.height = 0.25,      # Useful to change when you have multiple groups
+  break.x.by = 2,
+  ggtheme    = theme_bw(),       # Change ggplot2 theme
+  xlab       = 'Time in months', # Change X-axis label
+  title      = "Kaplan-Meier survival curve for PFS, Control arm (Invesigator Assessment)",
+  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
+)
+```
+
+```{r}
+# surv_data$Time <- surv_data$Time/12 # change time in months to years
+IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
+# times <- seq(0,5,by=1/12)
+times <- 0:3
+mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
+fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
+                    extrapolate = T, mods = mods) 
+```
+
+```{r}
+GoF_PFS <- data.frame(AIC = fit_PFS$AIC, BIC = fit_PFS$BIC)
+choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$AIC)]; choose_PFS
+choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$BIC)]; choose_PFS
+```
+
+```{r}
+mods=c("lnorm", "exp")
+fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
+                    extrapolate = T, mods=mods) 
+```
+
+```{r}
+N_sim <- 100
+fitted_PFS_chemo <- list()
+set.seed(1)
+for (i in 1:N_sim) {
+  ids <- sample(1:nrow(IPD_PFS), replace=T)
+  PFS_data_boot <- IPD_PFS[ids,]
+  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
+                     times = times, extrapolate = T, mods=c("lnorm"))
+  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$`log-Normal`
+  print(i)
+}
+save(fitted_PFS_chemo, file="fitted_PFS_control_firstline_investigator_lnorm_100.RData")
+```
+
+## Targeted arm
+
+```{r}
+time_interval <- seq(0, 36, by = 2)
+at_risk <- c(73,68,68,67,58,52,47,39,38,27,24,18,13,11,5,5,1,1,0)
+surv_data <- read.csv("Eric NEJM investigator digitized.csv", header = T)
+surv_data$St <- surv_data$St/100
+surv_data <- surv_data[surv_data$curve==2,]
+surv_data <- data.frame(k = 1:nrow(surv_data),
+                        Time = surv_data$time,
+                        Sk = surv_data$St)
+write.table(surv_data, file = "first_line_PFS_curve_targeted_investigator.txt", row.names = F)
+surv_data <- read.table("first_line_PFS_curve_targeted_investigator.txt", header = T)
+surv_times <- surv_data$Time
+
+n_risk_table <- create_at_risk_table(survival_time = surv_times,
+                                     Years = time_interval,
+                                     AtRisk = at_risk)
+write.table(n_risk_table, "first_line_PFS_risktable_targeted_investigator.txt", row.names = F)
+```
+
+```{r, results="hide"}
+# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
+digitise(surv_inp   = "first_line_PFS_curve_targeted_investigator.txt",
+         nrisk_inp  = "first_line_PFS_risktable_targeted_investigator.txt",
+         km_output  = "first_line_PFS_KM_targeted_investigator.txt",
+         ipd_output = "first_line_PFS_IPD_targeted_investigator.txt")
+
+# Link the IPD files across the two arms of the trial for OS and PFS
+IPD_PFS <- make.ipd(ipd_files = c("first_line_PFS_IPD_targeted_investigator.txt"), ctr = 1,
+                    var.labs  = c("time","event","arm"))
+IPD_PFS <- IPD_PFS %>% select(-arm)
+```
+
+```{r}
+library(survival)
+library(survminer)
+# Kaplan-Meier fit for PFS
+KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
+# plot KM for PFS
+ggsurvplot(
+  KM_PFS,
+  data       = IPD_PFS,
+  size       = 1,                # change line size
+  conf.int   = FALSE,            # Add confidence interval
+  pval       = F,                # Add p-value
+  risk.table = T,                # Add risk table
+  risk.table.height = 0.25,      # Useful to change when you have multiple groups
+  break.x.by = 2,
+  ggtheme    = theme_bw(),       # Change ggplot2 theme
+  xlab       = 'Time in months', # Change X-axis label
+title      = "Kaplan-Meier survival curve for PFS, Targeted arm (Investigator Assessment)",
+  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
+)
+```
+
+```{r}
+IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
+# times <- seq(0,5,by=1/12)
+times <- 0:3
+mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
+fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
+                    extrapolate = T, mods = mods)
+```
+
+```{r}
+GoF_PFS <- data.frame(AIC = fit_PFS$AIC, BIC = fit_PFS$BIC)
+choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$AIC)]; choose_PFS
+choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$BIC)]; choose_PFS
+```
+
+```{r}
+mods=c("exp", "lnorm", "llogis")
+fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
+                    extrapolate = T, mods=mods)
+```
+
+```{r}
+N_sim <- 100
+fitted_PFS_targeted <- list()
+set.seed(1)
+for (i in 1:N_sim) {
+  ids <- sample(1:nrow(IPD_PFS), replace=T)
+  PFS_data_boot <- IPD_PFS[ids,]
+  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
+                     times = times, extrapolate = T, mods=c("exp"))
+  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$Exponential
+  print(i)
+}
+save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_investigator_exp_100.RData")
+```
+
+```{r}
+N_sim <- 100
+fitted_PFS_targeted <- list()
+set.seed(1)
+for (i in 1:N_sim) {
+  ids <- sample(1:nrow(IPD_PFS), replace=T)
+  PFS_data_boot <- IPD_PFS[ids,]
+  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
+                     times = times, extrapolate = T, mods=c("lnorm"))
+  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$`log-Normal`
+  print(i)
+}
+save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_investigator_lnorm_100.RData")
+```
+
+```{r}
+
+```

### 2024-02-05 05_report/Manuscript_results_temp.Rmd
upload results combo prices

@@
   html_document: default
+  pdf_document: default
 ---
@@
 #rm(list = ls())
+options(scipen=999)
 ```
@@
 ```{r}
-#fileloc <- here::here("04_analysis","output","scenarios")
-#fileloc <- "/Users/davidrios/OneDrive - SickKids/tomacbook"
+fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime combo")
+nn <- 50
 ```
@@
 #res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
-res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:10]
+#res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:5]
+res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[1:nn]
 #res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
@@
          control = SoC) 
-
 ```
@@
                                `Total Cost` = "Total")) %>%
-  select(Variable, intervention, control, Delta , rr)
+  #select(Variable, intervention, control, Delta , rr)
+  select(Variable, intervention, control, Delta )
+tb2a$Variable <- as.character(tb2a$Variable)
+tb2a$Variable[tb2a$Variable=="Treatment"] <- "Targeted costs"
+tb2a$Variable[tb2a$Variable=="PLGG"] <- "Non-Targeted PLGG related costs"
+tb2a$Variable[tb2a$Variable=="AE"] <- "AE related costs"
+tb2a$Variable[tb2a$Variable=="Radiation"] <- "Radiation costs"
+tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
+                                                  "AE related costs","Targeted costs","Radiation costs"))
+pander(tb2a)
+```
 
-pander(tb2a)
+```{r}
+# Averaging cohort traces across simulation run
+l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[1:nn]
+prop_df  <- map_df(l_prop_df[1], readRDS) 
+prop_df$cycle <- as.numeric(prop_df$cycle)
+prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
+prop_df <- apply(prop_df,2,as.numeric)
+prop_df <- as.data.frame(prop_df)
+prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
+                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
+                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
+                                             "stroke_gen", "intervention")
+if (nn > 1) {
+  for (i in 2:nn) {
+    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
+    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
+    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
+    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
+                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
+                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
+                                             "stroke_gen", "intervention")
+    prop_df_i <- apply(prop_df_i,2,as.numeric)
+    prop_df_i <- as.data.frame(prop_df_i)
+    prop_df <- prop_df + prop_df_i
+  }
+  prop_df <- prop_df/nn
+}
+prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")
+
+prop_long <- prop_df %>% select(cycle, pre_prog, prog1, prog2, death_plgg, intervention) %>%
+  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
+  mutate(state=case_when(state=="pre_prog"~"Pre-progression",
+                         state=="prog1" ~ "1st progression",
+                         state=="prog2" ~ "2nd+ progression",
+                         state=="death_plgg" ~ "PLGG-related death"),
+         state=factor(state, levels=c("Pre-progression", "1st progression", "2nd+ progression", "PLGG-related death")),
+         cycle=cycle/12)
+ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
+  geom_line() +
+  labs(title = "Trace Plot of PLGG States Across Cycles",
+       x = "Year",
+       y = "Proportion",
+       color = "PLGG state") +
+  scale_color_manual(values = c("green","orange","red","navy")) + 
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) +
+  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, by = 10)) +
+  #geom_hline(yintercept=0.4, linetype="dashed", color = "purple") +
+  #geom_vline(xintercept=25, linetype="dashed", color = "purple") +
+  theme_bw() +
+  theme(legend.position = "right") + 
+  facet_wrap(~intervention)
+```
+
+```{r}
+# AEs
+l_AE_df <- list.files(paste0(fileloc, "/AE_track"),
+                      full.names = TRUE)[1:nn]
+AE_df <- map_df(l_AE_df[1], readRDS) 
+## Targeted
+AE_df_Targeted <- AE_df %>% filter(intervention == "Targeted")
+AE_prop_Targeted <-apply(AE_df_Targeted %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
+df_AE_Targeted <- data.frame(cycle=0:960)
+df_AE_Targeted$cycle <- as.factor(df_AE_Targeted$cycle)
+for (i in 1:length(AE_prop_Targeted)){
+  df_AE_prop <- as.data.frame(AE_prop_Targeted[[i]])
+  colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted)[i])
+  df_AE_Targeted <- df_AE_Targeted %>% left_join(df_AE_prop, by = c("cycle"))
+}
+df_AE_Targeted[1,-1] <- 0
+df_AE_Targeted$cycle <- as.numeric(df_AE_Targeted$cycle)
+df_AE_Targeted[is.na(df_AE_Targeted)] <- 0
+if (nn == 1) {
+  df_AE_Targeted$intervention <- "Targeted"
+}
+
+if (nn > 1) {
+  for (i in 2:nn) {
+    AE_df <- map_df(l_AE_df[i], readRDS) 
+    AE_df_Targeted_i <- AE_df %>% filter(intervention == "Targeted")
+    AE_prop_Targeted_i <-apply(AE_df_Targeted_i %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
+    df_AE_Targeted_i <- data.frame(cycle=0:960)
+    df_AE_Targeted_i$cycle <- as.factor(df_AE_Targeted_i$cycle)
+    for (j in 1:length(AE_prop_Targeted_i)){
+      df_AE_prop <- as.data.frame(AE_prop_Targeted_i[[j]])
+      colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted_i)[j])
+      df_AE_Targeted_i <- df_AE_Targeted_i %>% left_join(df_AE_prop, by = c("cycle"))
+    }
+    df_AE_Targeted_i[1,-1] <- 0
+    df_AE_Targeted_i$cycle <- as.numeric(df_AE_Targeted_i$cycle)
+    df_AE_Targeted_i[is.na(df_AE_Targeted_i)] <- 0
+    df_AE_Targeted <- df_AE_Targeted + df_AE_Targeted_i
+  }
+  df_AE_Targeted <- df_AE_Targeted/nn
+  df_AE_Targeted$intervention <- "Targeted"
+}
+## SoC
+AE_df_SoC <- AE_df %>% filter(intervention == "SoC")
+AE_prop_SoC <-apply(AE_df_SoC %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
+df_AE_SoC <- data.frame(cycle=0:960)
+df_AE_SoC$cycle <- as.factor(df_AE_SoC$cycle)
+for (i in 1:length(AE_prop_SoC)){
+  df_AE_prop <- as.data.frame(AE_prop_SoC[[i]])
+  colnames(df_AE_prop) <- c("cycle",names(AE_prop_SoC)[i])
+  df_AE_SoC <- df_AE_SoC %>% left_join(df_AE_prop, by = c("cycle"))
+}
+df_AE_SoC[1,-1] <- 0
+df_AE_SoC$cycle <- as.numeric(df_AE_SoC$cycle)
+df_AE_SoC[is.na(df_AE_SoC)] <- 0
+if (nn == 1) {
+  df_AE_SoC$intervention <- "SoC"
+}
+
+if (nn > 1) {
+  for (i in 2:nn) {
+    AE_df <- map_df(l_AE_df[i], readRDS) 
+    AE_df_SoC_i <- AE_df %>% filter(intervention == "SoC")
+    AE_prop_SoC_i <-apply(AE_df_SoC_i %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
+    df_AE_SoC_i <- data.frame(cycle=0:960)
+    df_AE_SoC_i$cycle <- as.factor(df_AE_SoC_i$cycle)
+    for (j in 1:length(AE_prop_SoC_i)){
+      df_AE_prop <- as.data.frame(AE_prop_SoC_i[[j]])
+      colnames(df_AE_prop) <- c("cycle",names(AE_prop_SoC_i)[j])
+      df_AE_SoC_i <- df_AE_SoC_i %>% left_join(df_AE_prop, by = c("cycle"))
+    }
+    df_AE_SoC_i[1,-1] <- 0
+    df_AE_SoC_i$cycle <- as.numeric(df_AE_SoC_i$cycle)
+    df_AE_SoC_i[is.na(df_AE_SoC_i)] <- 0
+    df_AE_SoC <- df_AE_SoC + df_AE_SoC_i
+  }
+  df_AE_SoC <- df_AE_SoC/nn
+  df_AE_SoC$intervention <- "SoC"
+}
+
+df_AE <- rbind(df_AE_Targeted, df_AE_SoC)
+
+prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
+  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
+  mutate(cycle=cycle/12)
+ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
+  geom_line() +
+  labs(title = "Trace Plot of PLGG-related AE States Across Cycles",
+       x = "Year",
+       y = "Proportion",
+       color = "PLGG-related AE states") +
+  theme_bw() +
+  theme(legend.position = "right") +
+  facet_wrap(~intervention) -> a
+
+prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
+                                intervention) %>%
+  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
+  mutate(cycle=cycle/12)
+ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
+  geom_line() +
+  labs(title = "Trace Plot of Other AE States Across Cycles",
+       x = "Year",
+       y = "Proportion",
+       color = "Other AE states") +
+  theme_bw() +
+  theme(legend.position = "right") +
+  facet_wrap(~intervention) -> b
+grid.arrange(a,b, nrow=2, ncol=1)
+```
+
+```{r}
+
 ```

### 2024-02-05 literature/plgg_OS_adjust.Rmd
upload results combo prices

---
title: "PLGG OS (prog to death) adjustment"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, eval = TRUE)
rm(list = ls())     # clear memory (removes all the variables from the workspace)
options(scipen=999) # disable scientific notation
```

```{r, warning=F, message=F}
if (!require('pacman')) install.packages('pacman'); library(pacman) # use this package to conveniently install other packages
# load (install if required) packages from CRAN
p_load("here", "dplyr", "devtools", "gems", "flexsurv", "flexsurvcure", "survHE", "survminer", "ggplot2", "msm", "igraph", "mstate", "reshape2", "knitr", "abind", "dampack", "data.table", "tm")

# load (install if required) packages from GitHub
# install_github("DARTH-git/darthtools", force = TRUE) Uncomment if there is a newer version
p_load_gh("DARTH-git/darthtools")
```

# 04 Digitized Data

Use the function `digitise()` to translate the digitised OS and PFS data into patient level information.

## Control arm

```{r}
time_interval <- c(0,5,10,15,20,25,30)
at_risk <- c(109,45,23,16,9,2,0)
surv_data <- read.csv("plgg_os_adjust.csv", header = T)
surv_data <- data.frame(k = 1:nrow(surv_data),
                        Time = surv_data$time,
                        Sk = surv_data$St)
write.table(surv_data, file = "plgg_os_adjust.txt", row.names = F)
surv_data <- read.table("plgg_os_adjust.txt", header = T)
surv_times <- surv_data$Time
n_risk_table <- create_at_risk_table(survival_time = surv_times,
                                     Years = time_interval,
                                     AtRisk = at_risk)
write.table(n_risk_table, "plgg_os_adjust_risktable.txt", row.names = F)
```

```{r, results="hide"}
# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
digitise(surv_inp   = "plgg_os_adjust.txt", 
         nrisk_inp  = "plgg_os_adjust_risktable.txt", 
         km_output  = "plgg_os_KM.txt", 
         ipd_output = "plgg_os_IPD.txt")

# Link the IPD files across the two arms of the trial for OS and PFS
IPD_PFS <- make.ipd(ipd_files = c("plgg_os_IPD.txt"), ctr = 1,
                    var.labs  = c("time","event","arm"))
IPD_PFS <- IPD_PFS %>% select(-arm)
```

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = F,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in years', # Change X-axis label
  title      = "Kaplan-Meier survival curve for OS, BRAF V600E patients",
  subtitle   = "Source: "
)
```

```{r}
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods) 
```

```{r}
GoF_PFS <- data.frame(AIC = fit_PFS$AIC, BIC = fit_PFS$BIC)
choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$AIC)]; choose_PFS
choose_PFS <- rownames(GoF_PFS)[which.min(GoF_PFS$BIC)]; choose_PFS
```

```{r}
mods=c("exp")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods=mods) 
```

```{r}
N_sim <- 100
fitted_os_adjusted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_os_adjusted[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_os_adjusted, file="fitted_plgg_os_adjust_exp_100.RData")
```

### 2024-02-05 03_ancilliary-functions/Costs.R

@@ -52,7 +52,12 @@ gen_costs <- function(){
   Costs_testing.l = list(FISH       = 0, # One-time cost (Supp table 1)
                          Nanostring = 0) # One-time cost (Supp table 1)
   
-  Costs_trt.l = list(Targeted = 3958.42*inflat * (1-discount) ) # monthly
+  Costs_trt.l = list(Targeted = 3958.42*inflat * (1-discount), # debraf
+                     tram = 76.96 * 30.44 * 1.3269 * (151.2/136.0)) # monthly
+  
+  # 76.96/day from Petros on teams, 1.3269 is average USD to CAD exchange rate in 2019 (Bank of Canada)
+  # 30.44 days a month
+  # StatsCan CPI 2022 vs. 2019 
   
   return(list(Inpatient_Costs.l   = Inpatient_Costs.l,
               Outpatient_costs.l  = Outpatient_costs.l,

### 2024-02-05 03_ancilliary-functions/Microsim.R

@@ -1,6 +1,6 @@
 Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_plgg,
                             Estimated_ae,AE_outside_mat,PrMortCardio_mat, SRS_mat1, cost_input,
-                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1, trt_duration ){
+                            util_input,uindx, rad_benefit, d.c,d.e,sim_numi, rri, loc_out1, trt_duration, combo ){
   # input:  
   # n.i: number of individuals
   # n.y: time horizon
@@ -94,6 +94,11 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
                     ncol = n.s,
                     dimnames = list(paste("ind", 1:n.i, sep = " "), v.n), data = F) 
     
+    # Tracking AE events (each cycle track the proportion of 1st entries)
+    v.n.AE <- v.n[-c(1:4)]
+    m.AE <- matrix(nrow = n.i, 
+                   ncol = length(v.n.AE),
+                   dimnames = list(paste("ind", 1:n.i, sep = " "), v.n.AE) ,data = 0)
     
     # Creating curent_age vector (Aware of spelling mistake but propogated through sub functions)
     # which is updated with the current age
@@ -113,8 +118,16 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
                                     Outpatient_costs = Outpatient_costs.l,
                                     m_Dur            = m.Dur,
                                     curent_age_v     = curent_age) 
+    
+    cost_trt <- Costs_trt.l$Targeted
+    if (combo == TRUE) {
+      cost_trt <- Costs_trt.l$Targeted + Costs_trt.l$tram
+    }
     if (intervention == "Targeted") { 
-      m.Costs.trt[,1] <- Costs_trt.l$Targeted
+      m.Costs.trt[,1] <- cost_trt
+    }
+    if (intervention == "Targeted" & combo == TRUE) {
+      m.Costs.trt[df_char$AgeDx >=6, 1] <- m.Costs.trt[df_char$AgeDx >=6, 1] + Costs_trt.l$tram # those >= 6 get another dose
     }
     
     # Utilities first cycle
[…]

### 2024-02-05 03_ancilliary-functions/Probs.R

@@ -72,6 +72,14 @@ Probs <- function( M_it, D_m,  df.i, Vis_m, CycleLength, GlobT, EstPLGG, EstAE,
                                         tt          = tt,
                                         trt_dur     = trt_dur)
   }
+  # test
+  # t_instate   = plgg.timeinstate+ CycleLength; 
+  # Cycle1      = CycleLength;
+  # StateIndx   = plgg.char;
+  # FlexSurvRes = EstPLGG;
+  # inter       = inter;
+  # tt          = tt;
+  # trt_dur     = trt_dur
   
   ## Radiation Benefit
   if(!(is.data.frame(rad_benefit1))){ # baseline
@@ -165,11 +173,17 @@ m.p.it[!RadIndc,c("neurologic","auditory","visual","stroke","cardiovascular","SN
     }
   }
   
+  # Apply hazard ratio of AE for targeted (for those who had never experienced chemo/only targeted)
+  if (inter == "Targeted" & any(M_it=="pre_prog")) {
+    reduced_AErisk <- M_it == "pre_prog"
+    m.p.it[reduced_AErisk, "neurologic"]     <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "neurologic"])     * (1/2.5)) 
+    m.p.it[reduced_AErisk, "auditory"]       <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "auditory"])       * (1/1.6))
+    m.p.it[reduced_AErisk, "visual"]         <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "visual"])         * (1/3.7))
+    m.p.it[reduced_AErisk, "stroke"]         <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "stroke"])         * (1/2.4))
+    m.p.it[reduced_AErisk, "cardiovascular"] <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "cardiovascular"]) * (1/5.3))
+  }
   
-  
-  # Calculate the probability of reamining in current state
-  
-  
+  # Calculate the probability of remaining in current state
   # Calculating the probability of remaining in state as 
   # 1 - sum(probability i leave to another state) 
   
@@ -179,7 +193,7 @@ m.p.it[!RadIndc,c("neurologic","auditory","visual","stroke","cardiovascular","SN
     }
   }
   
-  # Ensuringthat if death state you can't leave.
[…]

### 2024-02-05 03_ancilliary-functions/gen_synpop.R

@@ -23,7 +23,11 @@ gen_synpop <- function( n1=  100000, deter = T){
                                         -0.005295126, 0.0005518633, 0.0001718476,
                                         -0.02501394, 0.0001718476, 0.04914024), nrow = 3) )
     
-    AgeDx = round(runif(n = n1, min = 0,max = 18))
+    #AgeDx = round(runif(n = n1, min = 0,max = 18))
+    ages_under_6 <- runif(n1 * 0.27, min = 0, max = 6) # 27% < 6, Petros on teams
+    ages_over_6 <- runif(n1 - length(ages_under_6), min = 6, max = 18)
+    AgeDx <- c(ages_under_6, ages_over_6)
+    
     o1 <- exp(cbind(1, AgeDx) %*% t(coef1))
     Sex = rbinom(n1,1, prob = o1/(1+o1))
     o2 <- exp(cbind(1, AgeDx,Sex) %*% t(coef2))

### 2024-02-05 03_ancilliary-functions/microsim-helpers.R

@@ -49,7 +49,7 @@ Fun.GenI<- function(loc.analysis.set,NumToGen, Seed_n1){
 # SurvProbFun ####
 # This is the guts of the flexsurv summary function made to create probabilities
 # that are vectorized. Not commented if interested run once with debug
-SurvProbFun <- function(object, t , cycle1){
+SurvProbFun <- function(object, t , cycle1, calib = FALSE){
   start  = t - cycle1 
   x <- object
   dat <- x$data
@@ -71,6 +71,9 @@ SurvProbFun <- function(object, t , cycle1){
   
   basepars.mat <- flexsurv:::add.covs(x, x$res.t[dlist$pars, "est"], 
                                       beta, X[1, , drop = FALSE], transform = FALSE)
+  if (calib == T){ # calibrate risk of dying from plgg
+    basepars.mat <- basepars.mat/100
+  }
   basepars <- as.list(as.data.frame(basepars.mat))
   fncall[dlist$pars] <- basepars
   y <- do.call(fn, fncall)  
@@ -96,7 +99,7 @@ SurvProbFun <- function(object, t , cycle1){
 
 # rows 1,3,5,7,9 are associated with Fusion == 0
 
-Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, trt_dur){
+Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, trt_dur, calib){
   # Inputs
   # t_instate: time in current state, a vector
   # StateIndx: what state are they in
@@ -119,21 +122,23 @@ Probs.plggWT <- function(t_instate,StateIndx, Cycle1, FlexSurvRes, inter, tt, tr
 
   if(any(StateIndx ==  "pre_prog")){
     state1.log <- StateIndx ==  "pre_prog"
-    Prob.mat[state1.log,2] <- SurvProbFun(object = FlexSurvRes$flexobj[[arm]][[1]], t = t_instate[state1.log], cycle1 = Cycle1)
-    Prob.mat[state1.log,4] <- SurvProbFun(object = FlexSurvRes$flexobj[[3]][[1]],   t = t_instate[state1.log], cycle1 = Cycle1)
[…]

### 2024-02-05 04_analysis/Cost-effectiveness_basecase.R

@@ -2,7 +2,7 @@
 require(dplyr)
 require(here)
 require(pryr)
-
+library(darthtools)
 
 # location of files, and output 
 loc_here <- paste0(here::here(),"/")
@@ -15,6 +15,9 @@ dir.create(paste0(loc_here_out,"res_model"))
 dir.create(paste0(loc_here_out,"res_OS"))
 dir.create(paste0(loc_here_out,"res_tmat"))
 dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
 
 ## Required functions  ----
 ### Microsimulation.R Core of the microsimulation model 
@@ -103,23 +106,35 @@ dig_radbenefit1  <- readRDS(paste0(loc_here, "02_data/cherlow_dig.RDS"))
 
 k1 <- fun_genRadBenefit(dig_radbenefit =dig_radbenefit1, deter =T)
 
-## Survival curves
-# Targeted
-load(paste0(here::here("04_analysis","targeted survival"),"/fitted_PFS_targeted_swimmer.RData")) 
+### Survival curves
+## Targeted
+# Investigator assessment
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_exp_100.RData")) # pre-prog to prog1
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_lnorm_100.RData")) 
 
-# Control scenario 1
-load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk.RData")) 
-# Control scenario 2
-#load(paste0(here::here("04_analysis","control scenarios","Lianas paper PFS"),"/fitted_PFS_control_liana.RData")) 
-# Control scenario 3
-#load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data"),"/fitted_PFS_control_sk_firstline.RData")) 
-#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline.RData"))
+# Independent reviewer
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_exp_100.RData")) # pre-prog to prog1
[…]

### 2024-03-18 04_analysis/control scenarios/Erics firstline RCT/first_line_paper_survival.Rmd
updated

@@
 
+```{r}
+N_sim <- 100
+fitted_PFS_chemo <- list()
+set.seed(1)
+for (i in 1:N_sim) {
+  ids <- sample(1:nrow(IPD_PFS), replace=T)
+  PFS_data_boot <- IPD_PFS[ids,]
+  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
+                     times = times, extrapolate = T, mods=c("exp"))
+  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$Exponential
+  print(i)
+}
+save(fitted_PFS_chemo, file="fitted_PFS_control_firstline_investigator_exp_100.RData")
+```
+
 ## Targeted arm
@@
 ```
+
+```{r}
+
+```

### 2024-03-18 05_report/Manuscript_results_temp.Rmd
updated

@@
 ```{r}
-fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime combo")
-nn <- 50
+fileloc <- here::here("04_analysis","output","scenarios","sickkids control lnorm lifetime combo")
+index <- c(1:50)
 ```
@@
 #res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:5]
-res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[1:nn]
+res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
 #res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
@@
     mutate(Variable = factor(Variable, levels = c("LY","QALY","Cost")),
-         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE","Treatment","Radiation"))
+         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE","gen","Treatment","Radiation"))
          ) %>% 
@@
 tb2a$Variable[tb2a$Variable=="AE"] <- "AE related costs"
+tb2a$Variable[tb2a$Variable=="gen"] <- "General population costs"
 tb2a$Variable[tb2a$Variable=="Radiation"] <- "Radiation costs"
 tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
-                                                  "AE related costs","Targeted costs","Radiation costs"))
+                                                  "AE related costs" ,"General population costs", 
+                                                  "Targeted costs","Radiation costs"))
 pander(tb2a)
@@
 # Averaging cohort traces across simulation run
-l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[1:nn]
+l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[index]
 prop_df  <- map_df(l_prop_df[1], readRDS) 
@@
 l_AE_df <- list.files(paste0(fileloc, "/AE_track"),
-                      full.names = TRUE)[1:nn]
+                      full.names = TRUE)[index]
 AE_df <- map_df(l_AE_df[1], readRDS) 
@@
 
-df_AE <- rbind(df_AE_Targeted, df_AE_SoC)
+df_AE0 <- rbind(df_AE_Targeted, df_AE_SoC)
+df_AE <- as.data.frame(apply(df_AE0, 2, cumsum))
+df_AE$cycle <- df_AE0$cycle
+df_AE$intervention <- df_AE0$intervention
 
@@
   geom_line() +
-  labs(title = "Trace Plot of PLGG-related AE States Across Cycles",
+  labs(title = "Cumulative Incidence of PLGG-related AE States Across Cycles",
        x = "Year",
@@
   geom_line() +
-  labs(title = "Trace Plot of Other AE States Across Cycles",
+  labs(title = "Cumulative Incidence of Other AE States Across Cycles",
        x = "Year",
@@
 
-## Supplementary Table 1
+i## Supplementary Table 1
 

### 2024-03-18 03_ancilliary-functions/Microsim.R

@@ -76,6 +76,7 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
                                                                         dimnames = list(paste("ind", 1:n.i, sep = " "), 
                                                                         paste( 0:n.t)),data = 0)
     m.Costs.rad <- m.Costs.trt
+    m.Costs.ae.gen  <- m.Costs.ae
     
     # m.M (state tracking)
     m.M <- matrix(nrow = n.i, 
@@ -155,8 +156,6 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
       # m.Costs.rad[RadIndc, t + 1] <- 7199.34 # value given by Petros on Teams
       # df_char$Radiation[rad_switch] <- 1
       
-      # Check if patients have progressed and went to chemo
-      reduced_AErisk <- m.M[,t] == "pre_prog"
       
       # Create m.p: transition matrices for next period  
       m.p <- Probs(M_it              = m.M[,t], 
@@ -175,6 +174,7 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
                    inter             = intervention,
                    tt                = t,
                    trt_dur           = trt_duration)
+      
       #test
       # M_it              = m.M[,t];
       # D_m               = m.Dur;
@@ -215,9 +215,16 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
       # Capture first time patient enters an AE state
       m.Vis.AE <- m.Vis[,-c(1:4)]
       m.Vis.AE[m.Vis.AE==T] <- t # actual cycle, starts at cycle 1 not 0 for this thing only
+      
       for (j in 1:ncol(m.AE)){
         m.AE[m.AE[,j]==0,j] <- m.Vis.AE[m.AE[,j]==0,j]
       }
+
+      # Capture which state patient coming from when they first get into AE
+      # m.AE1 <- m.AE
+      # for (i in 1:nrow(m.M)) {
+      #   m.AE1[i,m.AE1[i,] > 0] <- m.M[i, m.AE[i,m.AE[i,] > 0]]
+      # }
       
[…]

### 2024-03-18 03_ancilliary-functions/Probs.R

@@ -173,16 +173,26 @@ m.p.it[!RadIndc,c("neurologic","auditory","visual","stroke","cardiovascular","SN
     }
   }
   
-  # Apply hazard ratio of AE for targeted (for those who had never experienced chemo/only targeted)
-  if (inter == "Targeted" & any(M_it=="pre_prog")) {
-    reduced_AErisk <- M_it == "pre_prog"
-    m.p.it[reduced_AErisk, "neurologic"]     <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "neurologic"])     * (1/2.5)) 
-    m.p.it[reduced_AErisk, "auditory"]       <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "auditory"])       * (1/1.6))
-    m.p.it[reduced_AErisk, "visual"]         <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "visual"])         * (1/3.7))
-    m.p.it[reduced_AErisk, "stroke"]         <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "stroke"])         * (1/2.4))
-    m.p.it[reduced_AErisk, "cardiovascular"] <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "cardiovascular"]) * (1/5.3))
+  # Apply hazard ratio of AE for targeted (for those who had never experienced chemo/only ever on targeted)
+  #if (inter == "Targeted" & any(M_it=="pre_prog")) {
+
+   if (inter == "Targeted"){
+     reduced_AErisk <- M_it == "pre_prog"
+   
+    # m.p.it[reduced_AErisk, "neurologic"]     <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "neurologic"])     * (1/2.5)) 
+    # m.p.it[reduced_AErisk, "auditory"]       <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "auditory"])       * (1/1.6))
+    # m.p.it[reduced_AErisk, "visual"]         <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "visual"])         * (1/3.7))
+    # m.p.it[reduced_AErisk, "stroke"]         <- 1-exp(-prob_to_rate(m.p.it[reduced_AErisk, "stroke"])         * (1/2.4))
[…]

### 2024-03-18 03_ancilliary-functions/summary.R

@@ -2,7 +2,7 @@
 
 # function of the following inputs
 sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
-                         costsplgg, costsAE, coststrt, costsrad, util, vRAD, vFusion  ){
+                         costsplgg, costsAE, costsgen, coststrt, costsrad, util, vRAD, vFusion  ){
   # What simulation number,
   # Parameter on radiation benefit
   # Intervention
@@ -73,9 +73,8 @@ sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
                           subset   = unlist(type), 
                           discount = 1)
   
-  costs_ae <- vector(mode = "numeric", length = 3)
-  
   # Costs AE 
+  costs_ae <- vector(mode = "numeric", length = 3)
   #   All 
   costs_ae[[1]] <-mean(rowSums(costsAE*v_dwc))
   #   Fused
@@ -86,6 +85,21 @@ sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
   df_costs_ae   <- tibble(Value    = costs_ae, 
                           Variable = "Cost", 
                           Type     = "AE",  
+                          subset   = unlist(type), 
+                          discount = 1)
+  
+  # Costs General
+  costs_gen <- vector(mode = "numeric", length = 3)
+  #   All 
+  costs_gen[[1]] <-mean(rowSums(costsgen*v_dwc))
+  #   Fused
+  costs_gen[[2]] <- mean(rowSums(costsgen[vFusion == 1,]*v_dwc))
+  #   Fused and Prog 1 
+  costs_gen[[3]] <- mean(rowSums(costsgen[vFusion == 1 & mVis[,2],]*v_dwc))
+  
+  df_costs_gen   <- tibble(Value    = costs_gen, 
+                          Variable = "Cost", 
+                          Type     = "gen",  
                           subset   = unlist(type), 
                           discount = 1)
   
@@ -121,7 +135,7 @@ sum_function <- function(sim_num, intervention1, rr1, d_rate,mM, mDur, mVis,
   
   # Costs Total
   #   All 
-  costs_total <- costs_ae + costs_plgg + costs_trt + costs_rad
+  costs_total <- costs_ae + costs_gen + costs_plgg + costs_trt + costs_rad
   
   df_costs_total <- tibble(Value    = costs_total, 
                            Variable = "Cost", 
[…]

### 2024-03-18 04_analysis/Cost-effectiveness_basecase.R

@@ -109,19 +109,23 @@ k1 <- fun_genRadBenefit(dig_radbenefit =dig_radbenefit1, deter =T)
 ### Survival curves
 ## Targeted
 # Investigator assessment
-#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_exp_100.RData")) # pre-prog to prog1
+load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_exp_100.RData")) # pre-prog to prog1
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_lnorm_100.RData")) 
 
 # Independent reviewer
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_exp_100.RData")) # pre-prog to prog1
-load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_lnorm_100.RData")) 
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_lnorm_100.RData")) 
 
 ## Control 
 # Investigator assessment
+load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_investigator_exp_100.RData")) # pre-prog to prog1
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_investigator_lnorm_100.RData")) # pre-prog to prog1
 
+# Independent reviewer
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_lnorm_100.RData")) # pre-prog to prog1
+
 # SickKids (control arm, match with only independent reviewer targeted)
-load(paste0(here::here("04_analysis","control scenarios","Bryans SickKids data firstline"),"/fitted_PFS_control_sk_firstline_exp_100.RData")) # pre-prog to prog 1     
[…]

### 2024-03-28 05_report/Manuscript_results_temp.Rmd
pushed

@@
 ```{r}
-fileloc <- here::here("04_analysis","output","scenarios","sickkids control lnorm lifetime combo")
-index <- c(1:50)
+fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime investigator combo")
+index <- c(1:30)
+nn <- length(index)
 ```
@@
 
-df_AE0 <- rbind(df_AE_Targeted, df_AE_SoC)
-df_AE <- as.data.frame(apply(df_AE0, 2, cumsum))
-df_AE$cycle <- df_AE0$cycle
-df_AE$intervention <- df_AE0$intervention
+df_AE_Targeted0 <- as.data.frame(apply(df_AE_Targeted, 2, cumsum))
+df_AE_Targeted0$cycle <- df_AE_Targeted$cycle
+df_AE_Targeted0$intervention <- df_AE_Targeted$intervention
+df_AE_SoC0 <- as.data.frame(apply(df_AE_SoC, 2, cumsum))
+df_AE_SoC0$cycle <- df_AE_SoC$cycle
+df_AE_SoC0$intervention <- df_AE_SoC$intervention
+df_AE <- rbind(df_AE_Targeted0, df_AE_SoC0)
 
@@
   theme_bw() +
+  scale_y_continuous(limits=c(0,0.5)) + 
   theme(legend.position = "right") +

### 2024-03-28 04_analysis/Cost-effectiveness_basecase.R

@@ -109,23 +109,23 @@ k1 <- fun_genRadBenefit(dig_radbenefit =dig_radbenefit1, deter =T)
 ### Survival curves
 ## Targeted
 # Investigator assessment
-load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_exp_100.RData")) # pre-prog to prog1
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_exp_100.RData")) # pre-prog to prog1
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_investigator_lnorm_100.RData")) 
 
 # Independent reviewer
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_exp_100.RData")) # pre-prog to prog1
-#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_lnorm_100.RData")) 
+load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_targeted_firstline_lnorm_100.RData")) 
 
 ## Control 
 # Investigator assessment
-load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_investigator_exp_100.RData")) # pre-prog to prog1
+#load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_investigator_exp_100.RData")) # pre-prog to prog1
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_investigator_lnorm_100.RData")) # pre-prog to prog1
 
 # Independent reviewer
 #load(paste0(here::here("04_analysis","control scenarios","Erics firstline RCT"),"/fitted_PFS_control_firstline_lnorm_100.RData")) # pre-prog to prog1
 
 # SickKids (control arm, match with only independent reviewer targeted)
[…]

### 2024-08-23 05_report/Manuscript_results_temp.Rmd
updated

@@
 fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime investigator combo")
-index <- c(1:30)
+index <- c(1:50)
 nn <- length(index)
@@
 prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
-                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
+                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual",      
+                                             "death_cardio",
                                              "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                              "stroke_gen", "intervention")
+p_surv <- p_surv_plgg <- as.data.frame(matrix(NA,nrow=nrow(prop_df), ncol=nn))
+p_surv$intervention  <- prop_df$intervention
+p_surv_plgg$intervention <- prop_df$intervention
+p_surv$cycle  <- prop_df$cycle
+p_surv_plgg$cycle <- prop_df$cycle
+p_surv[,1] <- 1 - (prop_df$death_outside + prop_df$death_cardio + prop_df$death_SN + prop_df$death_stroke +
+                  prop_df$death_plgg)
+p_surv_plgg[,1] <- 1 - prop_df$death_plgg
+
 if (nn > 1) {
@@
     prop_df <- prop_df + prop_df_i
+    # calculate overall survival
+    p_death_i <- prop_df_i$death_outside + prop_df_i$death_cardio + prop_df_i$death_SN + prop_df_i$death_stroke +
+                  prop_df_i$death_plgg
+    p_surv[,i] <- 1 - p_death_i
+    # calculate plgg-related survival
+    p_death_plgg_i <- prop_df_i$death_plgg
+    p_surv_plgg[,i] <- 1 - p_death_plgg_i
   }
@@
 grid.arrange(a,b, nrow=2, ncol=1)
+```
+
+```{r}
+# Survival
+## Overall
+p_surv$intervention <- ifelse(p_surv$intervention == 1, "Targeted", "SoC")
+p_surv1 <- data.frame(avg = apply(p_surv %>% select(-cycle, -intervention), 1, mean),
+                      lb = apply(p_surv %>% select(-cycle, -intervention), 1, function(x){quantile(x, 0.025)}),
+                      ub = apply(p_surv %>% select(-cycle, -intervention), 1, function(x){quantile(x, 0.975)}))
+p_surv1$intervention <- p_surv$intervention
+p_surv1$cycle <- p_surv$cycle/12
+ggplot(p_surv1, aes(x = cycle)) +
+  geom_ribbon(aes(ymin = lb, ymax = ub), fill = "blue", alpha = 0.2) +  
+  geom_line(aes(y = avg), color = "blue") +  
+  labs(x = "Time", y = "Survival Probability", 
+       title = "Overall Survival Over Time with 95% Confidence Interval") +
+  theme_bw() + facet_wrap(~intervention)
+
+## PLGG
+p_surv_plgg$intervention <- ifelse(p_surv_plgg$intervention == 1, "Targeted", "SoC")
+p_surv_plgg1 <- data.frame(avg = apply(p_surv_plgg %>% select(-cycle, -intervention), 1, mean),
+                      lb = apply(p_surv_plgg %>% 
+                                   select(-cycle, -intervention), 1, function(x){quantile(x, 0.025)}),
+                      ub = apply(p_surv_plgg %>% 
+                                   select(-cycle, -intervention), 1, function(x){quantile(x, 0.975)}))
+p_surv_plgg1$intervention <- p_surv_plgg$intervention
+p_surv_plgg1$cycle <- p_surv_plgg$cycle/12
+ggplot(p_surv_plgg1, aes(x = cycle)) +
+  geom_ribbon(aes(ymin = lb, ymax = ub), fill = "blue", alpha = 0.2) +  
+  geom_line(aes(y = avg), color = "blue") +  
+  labs(x = "Time", y = "surv_plggival Probability", 
+       title = "PLGG-related survival Over Time with 95% Confidence Interval") +
+  theme_bw() + facet_wrap(~intervention)
 ```

### 2024-08-23 05_report/Manuscript_results_temp1.Rmd
updated

---
title: "Manuscript Results"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
#rm(list = ls())
options(scipen=999)
```

```{r required packages}
require(tidyverse)    # for data manipulation
require(formattable)  # for formatting tables
require(knitr)        # for saving tables
require(scales)       # for ggplot axis labels
library(gridExtra)    # for gridded plots 
require(survival)     # for survival analysis
require(survminer)    # for survival plotting
require(kableExtra)
index <- c(1:50)
nn <- length(index)
loc_here <- paste0(here::here(),"/")
source(paste0(loc_here,"05_report/report_functions.R"))
```

# Base case

## Scenario #1a

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy 
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated) 
- 100% combo price
- Discount rate: 1.5 
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023. 
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm 
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("basecase/","1a")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1c

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **50% combo price reduction**
- Discount rate: 1.5
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("basecase/","1c")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1d

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **75% combo price reduction**
- Discount rate: 1.5
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("basecase/","1d")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1e

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- 100% combo price
- Discount rate: 1.5
- **Data source for controls: n=34 SickKids controls**
- **Data source for exposed: Investigator assessment - Bouffet et al., NEJM 2023.**
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("basecase/","1e")
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

# 0% discount rate

## Scenario #1a

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy 
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated) 
- 100% combo price
- Discount rate: 0 
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023. 
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm 
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("0_dr/","1a")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1c

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **50% combo price reduction**
- Discount rate: 0
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("0_dr/","1c")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1d

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **75% combo price reduction**
- Discount rate: 0
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("0_dr/","1d")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1e

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- 100% combo price
- Discount rate: 0
- **Data source for controls: n=34 SickKids controls**
- **Data source for exposed: Investigator assessment - Bouffet et al., NEJM 2023.**
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("0_dr/","1e")
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

# 3% discount rate

## Scenario #1a

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy 
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated) 
- 100% combo price
- Discount rate: 3
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023. 
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm 
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("3_dr/","1a")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1c

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **50% combo price reduction**
- Discount rate: 3
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("3_dr/","1c")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1d

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **75% combo price reduction**
- Discount rate: 3
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("3_dr/","1d")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1e

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- 100% combo price
- Discount rate: 3
- **Data source for controls: n=34 SickKids controls**
- **Data source for exposed: Investigator assessment - Bouffet et al., NEJM 2023.**
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("3_dr/","1e")
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

# 20% radiated at subsequent progression

## Scenario #1a

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy 
- 20% radiation at progression
- 100% combo price
- Discount rate: 1.5 
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023. 
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm 
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("rad/","1a")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1c

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 20% radiation at progression
- **50% combo price reduction**
- Discount rate: 1.5
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("rad/","1c")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1d

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 20% radiation at progression 
- **75% combo price reduction**
- Discount rate: 1.5
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("rad/","1d")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1e

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 20% radiation at progression 
- 100% combo price
- Discount rate: 1.5
- **Data source for controls: n=34 SickKids controls**
- **Data source for exposed: Investigator assessment - Bouffet et al., NEJM 2023.**
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("rad/","1e")
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

# 2-year treatment duration - Basecase

## Scenario #1a

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy 
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated) 
- 100% combo price
- Discount rate: 1.5 
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023. 
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm 
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("twoyr/","1a")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1c

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **50% combo price reduction**
- Discount rate: 1.5
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("twoyr/","1c")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1d

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- **75% combo price reduction**
- Discount rate: 1.5
- Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("twoyr/","1d")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1e

- Combo vs. chemo as first-line treatment
- Lifetime duration of combo therapy
- 0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
- 100% combo price
- Discount rate: 1.5
- **Data source for controls: n=34 SickKids controls**
- **Data source for exposed: Investigator assessment - Bouffet et al., NEJM 2023.**
- **Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
- 10,000 individuals
- 50 simulation runs

\newpage

### Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("twoyr/","1e")
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
fileloc <- here::here("04_analysis","output","scenarios",scen, "sickkids control invest lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
grid.arrange(plots$ae_plot1, plots$ae_plot2, nrow=2)
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

### 2024-08-23 03_ancilliary-functions/Costs.R

@@ -6,7 +6,7 @@ gen_costs <- function(){
   # output: a list with Inpatient_Costs.l , Outpatient_costs.l, AE_costs.l, Lookback_costs.l
   # see 06_report, Tables_out for source of values
   inflat <- 151.2/133.4 # StatsCan CPI 2022 vs. 2018
-  discount <- 0 # x% discount, e.g. 20% discount = 0.2
+  discount <- 0.75 # x% discount, e.g. 20% discount = 0.2
   
   Inpatient_Costs.l  <- list(
     pre_prog = c(14955.52, 357.26)*inflat, # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)
@@ -53,7 +53,7 @@ gen_costs <- function(){
                          Nanostring = 0) # One-time cost (Supp table 1)
   
   Costs_trt.l = list(Targeted = 3958.42*inflat * (1-discount), # debraf
-                     tram = 76.96 * 30.44 * 1.3269 * (151.2/136.0)) # monthly
+                     tram = 76.96 * 30.44 * 1.3269 * (151.2/136.0) * (1-discount)) # monthly
   
   # 76.96/day from Petros on teams, 1.3269 is average USD to CAD exchange rate in 2019 (Bank of Canada)
   # 30.44 days a month

### 2024-08-23 03_ancilliary-functions/Microsim.R

@@ -149,14 +149,6 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
       #if(t == 100){debug(Probs)}
       # if(any(m.Vis[,2] & df_char$Radiation == 1)){debug(Probs)}
       
-      ### Move those after 2nd prog to rad and stop chemo/targeted
-      # rad_switch <- m.M[,t] == "prog2"
-      # RadIndc <- rad_switch & df_char$Radiation == 0 # indicated for Rad switch and never incurred Rad cost
-      # #Cost of radiation incurred at the switch to rad
-      # m.Costs.rad[RadIndc, t + 1] <- 7199.34 # value given by Petros on Teams
-      # df_char$Radiation[rad_switch] <- 1
-      
-      
       # Create m.p: transition matrices for next period  
       m.p <- Probs(M_it              = m.M[,t], 
                    D_m               = m.Dur, 
@@ -205,6 +197,26 @@ Microsimulation <- function(n.i, n.y, cyc.t, monitor,seed_n, df_char,Estimated_p
       # Tests to ensure that samplev is working 
       if(any(m.M[, t + 1] == "cardiovascular_gen" & m.M[, t ] == "cardiovascular")){ 
         stop("returning to state")}
+      
+      ### Move 20% to rad who had just progressed and stop chemo/targeted
+      # rad_switch <- (m.M[,t]=="pre_prog" & m.M[,t+1]=="prog1") | (m.M[,t]=="prog1" & m.M[,t+1]=="prog2")
+      # 
+      # # Identify indices of TRUE values
+      # true_indices <- which(rad_switch == TRUE)
+      # # Calculate 20% of these TRUE indices
+      # num_true_remain <- ceiling(0.20 * length(true_indices))
+      # # Randomly shuffle the TRUE indices
+      # shuffled_true_indices <- sample(true_indices)
+      # # Select the first 20% to remain TRUE
+      # indices_remain_true <- shuffled_true_indices[1:num_true_remain]
+      # # Create a new vector that sets all other TRUEs to FALSE
+      # rad_switch1 <- rad_switch  # Start with the original vector
+      # rad_switch1[-indices_remain_true] <- FALSE  # Set all except the chosen 20% to FALSE
+      # 
+      # RadIndc <- rad_switch1 & df_char$Radiation == 0 # indicated for Rad switch and never incurred Rad cost
+      # # Cost of radiation incurred at the switch to rad
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_basecase.R

@@ -1,264 +1,0 @@
-### R Script for running cost-effectiveness analysis 
-require(dplyr)
-require(here)
-require(pryr)
-library(darthtools)
-
-# location of files, and output 
-loc_here <- paste0(here::here(),"/")
-loc_here_out <- paste0(here::here(),"/04_analysis/output/")
-
-# create folders in the location of the output
-dir.create(loc_here_out)
-dir.create(paste0(loc_here_out,"res_rad"))
-dir.create(paste0(loc_here_out,"res_model"))
-dir.create(paste0(loc_here_out,"res_OS"))
-dir.create(paste0(loc_here_out,"res_tmat"))
-dir.create(paste0(loc_here_out,"res_CI"))
-dir.create(paste0(loc_here_out,"trace"))
-dir.create(paste0(loc_here_out,"AE_track"))
-
-
-## Required functions  ----
-### Microsimulation.R Core of the microsimulation model 
-source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
-
-## Sourcing functions ----
-source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
-# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
-# EstProbs.AE: estimated AE probabilities
-# EstProbs.plgg: estimates PLGG probs
-# FunFlexFit: helper
-# FunFlexFit_AE: helper
-
-source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
-# Helpers for Probs and Microsimulation functions
-#Fun.GenI: Bootstrap wrapper to generate sample population
-#fun_index: given a time from an event and returns the index of how many cycles since 0
-#Probs.plggFused:  Probs helper
-#Probs.plggWT:  Probs helper
-#Probs.trtNoRad: Probs helper
-#Probs.trtRad: Probs helper
-#samplev2: used to estimate probabilities
-#SurvProbFun: flexsurv objects to probabilities
-
-source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
-# AE non treatment related function
-#AE_outside_pr: Generates matrix of probability of having various AE
-#MortCardio_est: Probability of death related to Cardiovascular event
-#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_indep_exp.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1d"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_indep_lnorm.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1d"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_invest_exp_exp.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1d"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_invest_lnorm_exp.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1d"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_invest_lnorm_lnorm.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1d"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_scenario.R

@@ -1,215 +1,0 @@
-### R Script for running cost-effectiveness analysis 
-require(dplyr)
-require(here)
-require(pryr)
-
-
-# location of files, and output 
-loc_here <- paste0(here::here(),"/")
-loc_here_out <- paste0(here::here(),"/04_analysis/outputscenario/")
-
-# create folders in the location of the output
-dir.create(loc_here_out)
-dir.create(paste0(loc_here_out,"res_rad"))
-dir.create(paste0(loc_here_out,"res_model"))
-dir.create(paste0(loc_here_out,"res_OS"))
-dir.create(paste0(loc_here_out,"res_tmat"))
-dir.create(paste0(loc_here_out,"res_CI"))
-
-## Required functions  ----
-### Microsimulation.R Core of the microsimulation model 
-source(paste0(loc_here,"03_ancilliary-functions/MicrosimScenario.R"))
-
-## Sourcing functions ----
-source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
-# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
-# EstProbs.AE: estimated AE probabilities
-# EstProbs.plgg: estimates PLGG probs
-# FunFlexFit: helper
-# FunFlexFit_AE: helper
-
-source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
-# Helpers for Probs and Microsimulation functions
-#Fun.GenI: Bootstrap wrapper to generate sample population
-#fun_index: given a time from an event and returns the index of how many cycles since 0
-#Probs.plggFused:  Probs helper
-#Probs.plggWT:  Probs helper
-#Probs.trtNoRad: Probs helper
-#Probs.trtRad: Probs helper
-#samplev2: used to estimate probabilities
-#SurvProbFun: flexsurv objects to probabilities
-
-source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
-# AE non treatment related function
-#AE_outside_pr: Generates matrix of probability of having various AE
-#MortCardio_est: Probability of death related to Cardiovascular event
-#PrDeath_SM: Probability of death realted to SMN event
-#PrDeath_Stroke: Probability of death related to stroke AE
-#RSR_gen: ratios of RSR ratios 
-
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_sickkids_invest_exp.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1e"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 04_analysis/Cost-effectiveness_sickkids_invest_lnorm.R

@@ -1,0 +1,266 @@
+### R Script for running cost-effectiveness analysis 
+require(dplyr)
+require(here)
+require(pryr)
+library(darthtools)
+
+scen <- "1e"
+
+# location of files, and output 
+loc_here <- paste0(here::here(),"/")
+loc_here_out <- paste0(here::here(),"/04_analysis/output/")
+
+# create folders in the location of the output
+dir.create(loc_here_out)
+dir.create(paste0(loc_here_out,"res_rad"))
+dir.create(paste0(loc_here_out,"res_model"))
+dir.create(paste0(loc_here_out,"res_OS"))
+dir.create(paste0(loc_here_out,"res_tmat"))
+dir.create(paste0(loc_here_out,"res_CI"))
+dir.create(paste0(loc_here_out,"trace"))
+dir.create(paste0(loc_here_out,"AE_track"))
+
+
+## Required functions  ----
+### Microsimulation.R Core of the microsimulation model 
+source(paste0(loc_here,"03_ancilliary-functions/Microsim.R"))
+
+## Sourcing functions ----
+source(paste0(loc_here, "03_ancilliary-functions/Fun_surv_est.R"))
+# Fun_surv_est.R functions to estimate PLGG and treatment related AE probailities 
+# EstProbs.AE: estimated AE probabilities
+# EstProbs.plgg: estimates PLGG probs
+# FunFlexFit: helper
+# FunFlexFit_AE: helper
+
+source(paste0(loc_here,"03_ancilliary-functions/microsim-helpers.R"))
+# Helpers for Probs and Microsimulation functions
+#Fun.GenI: Bootstrap wrapper to generate sample population
+#fun_index: given a time from an event and returns the index of how many cycles since 0
+#Probs.plggFused:  Probs helper
+#Probs.plggWT:  Probs helper
+#Probs.trtNoRad: Probs helper
+#Probs.trtRad: Probs helper
+#samplev2: used to estimate probabilities
+#SurvProbFun: flexsurv objects to probabilities
+
+source(paste0(loc_here,"03_ancilliary-functions/ae_functions.R"))
+# AE non treatment related function
+#AE_outside_pr: Generates matrix of probability of having various AE
+#MortCardio_est: Probability of death related to Cardiovascular event
+#PrDeath_SM: Probability of death realted to SMN event
[…]

### 2024-08-23 05_report/report_functions.R

@@ -1,0 +1,386 @@
+create_table <- function(model_object) {
+  res_model <- model_object
+  
+  # turning into dataframe
+  df_model  <- map_df(res_model, readRDS) 
+  df_model <- df_model %>% filter(subset == "all")
+  # creating a key in the same format as the one in correct_surv
+  df_model <- df_model %>% 
+    mutate(key = paste0(sim,"_",rr))
+  
+  # fixing survival for everyone who doesn't have a correct survival time
+  df_model <- df_model %>% 
+    mutate( Value = ifelse(Variable == "LY", 80-Value, Value))
+  
+  # no longer need key 
+  df_model <- df_model %>%
+    select(-key)
+  
+  df_output <- df_model %>% filter(discount == 1) %>% select(-rr)
+  # df_output$intervention[df_output$intervention == "SoC"] <- "Targeted"
+  df_output1 <- df_output %>% group_by(Variable, Type) %>% summarise(Mean = mean(Value))
+  #write.csv(df_output1, "output.csv", row.names = F)
+  
+  df_delta <- df_model %>% 
+    spread(intervention, Value) %>%   
+    mutate(Delta = Targeted-SoC) %>% 
+    select(-Targeted,-SoC)
+  
+  df_model <- df_model %>% 
+    group_by(Variable, Type, subset, intervention, discount, rr) %>% 
+    summarise( mean = mean(Value),
+               q025 = quantile(Value, 0.025),
+               q975 = quantile(Value, 0.975)) %>% ungroup()
+  df_model <-df_model %>% 
+    mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean,
+                                                                symbol = "$" ,digits = 0)),
+                            Variable != "Cost"~ paste0(round(mean, 2))),
+           q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "$" ,digits = 0)),
+                            Variable != "Cost"~ paste0(round(q025, 2))),
+           q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "$" ,digits = 0)),
+                            Variable != "Cost"~ paste0(round(q975, 2))                  
+           )
+    ) %>% 
+    mutate( stat = paste0(mean, " (", q025, ";",q975,")"))
+  
[…]

### 2024-08-28 03_ancilliary-functions/Costs.R
updated

@@ -6,7 +6,7 @@ gen_costs <- function(){
   # output: a list with Inpatient_Costs.l , Outpatient_costs.l, AE_costs.l, Lookback_costs.l
   # see 06_report, Tables_out for source of values
   inflat <- 151.2/133.4 # StatsCan CPI 2022 vs. 2018
-  discount <- 0.75 # x% discount, e.g. 20% discount = 0.2
+  discount <- 0 # x% discount, e.g. 20% discount = 0.2
   
   Inpatient_Costs.l  <- list(
     pre_prog = c(14955.52, 357.26)*inflat, # Cycle 1; cycle 2 until patient is 18 years old (Supp table 1)

### 2024-08-28 04_analysis/Cost-effectiveness_indep_exp.R

@@ -4,7 +4,7 @@ require(here)
 require(pryr)
 library(darthtools)
 
-scen <- "1d"
+scen <- "1a"
 
 # location of files, and output 
 loc_here <- paste0(here::here(),"/")
@@ -204,7 +204,7 @@ for(sim_num1 in torun1){
                          sim_numi         = sim_num, 
                          rri              = 0,
                          loc_out1         = loc_here_out,
-                         trt_duration     = 2,
+                         trt_duration     = 1,
                          combo            = TRUE)
   
   # # # Testing

### 2024-08-28 05_report/report_functions.R

@@ -109,8 +109,37 @@ create_table <- function(model_object) {
   tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
                                                     "Late effect costs" ,"General population costs", 
                                                     "Targeted costs","Radiation costs"))
-  return(kable(tb2a, format="latex", booktabs=TRUE) %>% 
-           kable_styling(latex_options=c("scale_down","HOLD_position")))
+  
+  # CEAC
+  df_deltacea1 <- df_deltacea %>%
+    mutate(rr =factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit")),
+           type = "all")
+  df_means <- df_deltacea %>%
+    group_by(rr) %>%
+    summarise(Cost = mean(Cost),
+              QALY = mean(QALY)) %>%
+    mutate(type = "Mean Values") %>%
+    mutate(rr1 = factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit") ))
+  toplot_plane <-df_deltacea1 %>%
+    ggplot() +
+    geom_point(aes(x = QALY, y = Cost), alpha = 0.75 , size = 0.6) +
+    # geom_point(aes(x = QALY, y = Cost), color = "black", data = df_means,shape = 2,show.legend = TRUE, size = 3) +
+    geom_hline(yintercept = 0) +
+    geom_vline(xintercept = 0) +
+    theme_bw() +
+    theme(legend.title = element_blank()) +
+    labs(color = "", shape = "Mean",  
+         y="Discounted Total Costs",
+         x="Discounted QALYs",
+         title = "Cost-Effectiveness Acceptability Curve (CEAC)") +
+    scale_y_continuous(labels = dollar_format(prefix="$")) +
+    #facet_wrap(~ rr) +
+    theme( panel.grid.major = element_blank(),
+           panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
+  tablee <- kable(tb2a, format="latex", booktabs=TRUE) %>% 
+    kable_styling(latex_options=c("scale_down","HOLD_position"))
+  return(list(a=tablee,
+         b=toplot_plane))
 }
 
 create_trace <- function(fileloc) {
@@ -291,15 +320,16 @@ create_trace <- function(fileloc) {
[…]
